\chapter{Cloud Computing Fundamentals}
\label{sec:icloud-fundamentals}

\FILENAME

\begin{comment}
  \section{Overview - Completly outdated as old content of class}

  % 6 Video lectures {48 minutes 20 seconds}
  
  The information in this section has been collected by Prof. Judy Qiu
  and taught at INdiana University. The first lecture introduces you
  to the schedule and homework submissions. Key cloud computing topics
  are highlighted. A selection of recommended and required textbooks
  is given, followed by an overview of the course structure. Please
  note that this section will change.

  \video{Cloud}{13:13}{Overview}{https://www.youtube.com/watch?v=Kde5YVUwDTQ}

  \slides{Cloud}{Page 1}{Overview}{https://drive.google.com/open?id=0B88HKpainTSfYjU4QzdDSms0Nk0}

PPT ARE DIFFERNT FROM VIDEO!!! 

  \slides{Cloud}{Page 1}{Overview - pptx}{https://drive.google.com/open?id=0B88HKpainTSfV3p0RUd1REtVTGs}

\end{comment}

\section{Introduction}

Changes in computing technology for the past five decades are discussed.
The rise of Big Data is shown in terms of its growth and significance. A
prediction is made that the paradigm which has held `til now of
individual researchers with personal computers will give way to
communities of researchers organizing through clouds. A more in-depth
look at Unit 1 follows, focusing on the chapters from Distributed and
Cloud Computing: From Parallel Processing to the Internet of Things.

% Note that the following lectures are replaced by:
%
% Geoffrey's updated 22 lectures for e222 and cloud intro e516/616
% main location is at https://drive.google.com/drive/u/5/folders/1WLHvJ8qkJiXGC9NnOceTH9ZdFngC-xoO


\video{Cloud}{14:48}{Introduction - Part A
  (Updated)}{https://drive.google.com/open?id=16gPOZ7EK6iaac2B-9KbM3OHITqHT8YxG}
\slides{Cloud}{}{Introduction - Part A (Updated)}{https://drive.google.com/open?id=17_voZxBdqiLicJKzroQ2DzjW4zvp0VYb}

This lecture introductes you to the following concepts: Cloud
definitions (AWS, AZURE,etc) , Virtualization, Hype Cycle, Cloud
infrastructure, Cloud software, Clouds and Parallel computing,
Storage, HPC clouds, Jobs, Future Issues, and Fault tolerance.


\video{Cloud}{20:22}{Part B (Updated)}{https://drive.google.com/open?id=1iGv6GG2b2th_RL3kQX6P04Y0AyuUxQcj}
\slides{Cloud}{}{Part B (Updated)}{https://drive.google.com/open?id=1SJZblEkhjgQBCDaDSiSCaXTLVPx_X8m4}

This lecture introductes you to the following concepts: FAAS, Cloud
HPC, HPC-FAAS, public clouds, IOT, service oriented systems, cloud and
infrastructure description, virtualization in detail, Google and
microsoft cloud use cases, and Renting idle clouds.

\video{Cloud}{20:45}{Part C (Updated)}{https://drive.google.com/open?id=1nU9HlqDe_vEZR1MlOq2XibnoHmaygo-H}
\slides{Cloud}{}{Part C (Updated)}{https://drive.google.com/open?id=1Thg2yOnKBQKdndgdItpviGw0hhxjY2K2}

This lecture introductes you to the following concepts: more on
clouds, Messaging model, SOA, FAAS, SAAS, PAAS, NAAS, etc. Garner
remarks on clouds, and Server computing.


 \video{Cloud}{9:08}{Part D (Updated)}{https://drive.google.com/open?id=1Qayxfwuc_qSeCzaIpHj3-F0N7TONvM5L}
\slides{Cloud}{}{Part D (Updated)}{https://drive.google.com/open?id=1EsHbUn7xdjTrLXmY8HCIhZqLaWeODD_1}

This lecture introductes you to the following concepts: World wide
cloud market, IT growth by areas, IT infrastructure development,
Comparing Amazon and Cloud computing expenditures.

 \video{Cloud}{11:21}{Part E (Updated)}{https://drive.google.com/open?id=1EC-eOYuBOV1qMojSg4Mg50doPqjAY0Hr}
\slides{Cloud}{}{Part E (Updated)}{https://drive.google.com/open?id=1K3RzVlfiwZAqwhCPxNEP8Q1JNxyOZhrv}

This lecture introductes you to the following concepts: Virtualization
in detail, Areas covered by Open Stack, and Virtualization technologies.

 \video{Cloud}{13:41}{Part F (Updated)}{https://drive.google.com/open?id=1_M0HDemFmykAq4iPuQ0MHYIW0kffHuMa}
\slides{Cloud}{}{Part F (Updated)}{https://drive.google.com/open?id=18deLUm2zGlHcHHbyVhecwSf52RHAq9VT}

This lecture introductes you to the following concepts: Emerging
trends Move along hype cycle. Emerging technologies, Gartner priority
matrix for Emerging Technologies, Gartner Hype cycle for data center
infrastructure.

 \video{Cloud}{16:05}{Part G (Updated)}{https://drive.google.com/open?id=19k6os58_OCCsmbusWQ6z6n9hwVmmd163}
\slides{Cloud}{}{Part G (Updated)}{https://drive.google.com/open?id=1ZD-h-dmQgAFROBEI1KMJROTxPVPAJ_P_}

This lecture introductes you to the following concepts: Gartner Hype
Cycle for technology emerging 2008, Gartner priority matrix for
emerging tech in 2008-2015, Digital business (Web, E- business, etc),
digital marketing, digital business, and Autonomous.

 \video{Cloud}{13:22}{Part H (Updated)}{https://drive.google.com/open?id=1_lH7ou_UQOMMfdSSQLrqZr8yJZIr7rC0}
\slides{Cloud}{}{Part H (Updated)}{https://drive.google.com/open?id=1WOlwFtHNvFSaQX9WAXBwO2q1qsvBM6Yd}

This lecture introductes you to the following concepts: Cloud
infrastructure, Azure cloud data centers, Google cloud data centers,
IBM cloud data centers, Green clouds, Cloud and HPC

 \video{Cloud}{13:13}{Part I (Updated)}{https://drive.google.com/open?id=1UwBzSKK-iHYW7aRCS_f4BoXNYxUb476i}
\slides{Cloud}{}{Part I (Updated)}{https://drive.google.com/open?id=1_1fL2L-tpjlL7og49XDxH_HLPD6Tupik}

This lecture introductes you to the following concepts: Cloud
infrastructure Gartner view 2017, Containers vs virtual
machines. Serverless computing domain. Key trends in computer
infrastructure, and AI on data centers.

 \video{Cloud}{37:56}{Part J (Updated)}{https://drive.google.com/open?id=1tasT1lJE_7pwowuk0D68M7rgW1gtv3im}
\slides{Cloud}{}{Part J (Updated)}{https://drive.google.com/open?id=1DKshrkb2bMOt5p0H2YDkOZhekAFIx5nJ}

 \video{Cloud}{11:58}{Part K (Updated)}{https://drive.google.com/open?id=1BzpXNqs3Ai_QlSsjxSV6Q3FevZt1BPj-}
\slides{Cloud}{}{Part K (Updated)}{https://drive.google.com/open?id=1dQbzoVwDoqqnwSO8eHmu_WfiU2FVXtLL}

 \video{Cloud}{13:03}{Part L (Updated)}{https://drive.google.com/open?id=1pIjcar6SZSelWiR6dv4lhnsmweDarNXR}
\slides{Cloud}{}{Part L (Updated)}{https://drive.google.com/open?id=10bAckYz455Yd5tqDGpwkMZUmDn9FKl0n}

 \video{Cloud}{24:12}{Part M (Updated)}{https://drive.google.com/open?id=16rb0zZafTLoYhT638qc4IRorOk5qgRP-}
\slides{Cloud}{}{Part M (Updated)}{https://drive.google.com/open?id=1TPgbfK6PhWjyr3u115Pq4jTPNPo2JU70}

 \video{Cloud}{35:46}{Part N (Updated)}{https://drive.google.com/open?id=1apuvCaKlQBZp8FjvqN9It5bJhfXmf1kg}
\slides{Cloud}{}{Part N (Updated)}{https://drive.google.com/open?id=1lBmpMry2FXwEjf93EMJPNDpw_G-yUcI1}

 \video{Cloud}{19:22}{Part O (Updated)}{https://drive.google.com/open?id=1_A51jrlzKYKhQvefXbJPs0J4GiCCQ1et}
\slides{Cloud}{}{Part O (Updated)}{https://drive.google.com/open?id=1JvIK-J4HUSvexmNKbBV_fdN8xvGBylR2}

 \video{Cloud}{19:29}{Part P (Updated)}{https://drive.google.com/open?id=1u5z9-GY1Hecp8nR47Gxe8506NnhHduF1}
\slides{Cloud}{}{Part P (Updated)}{https://drive.google.com/open?id=1ECR-m-pgW_7JnNDJ9ZLDYpicRrtxawwF}

 \video{Cloud}{16:19}{Part Q (Updated)}{https://drive.google.com/open?id=1vmtpndTlmtV4DzUtl04_nWo9DCR84mIM}
\slides{Cloud}{}{Part Q (Updated)}{https://drive.google.com/open?id=1u_rugpZg6m2x0B7r4kifEUxMej71-wMh}

 \video{Cloud}{4:52}{Part R (Updated)}{https://drive.google.com/open?id=1JMNPLdbS81Hfi5P7irDUy7kna35jpU6j}
\slides{Cloud}{}{Part R (Updated)}{https://drive.google.com/open?id=1Sev0VF7tDZo4Oxa_ghk6b4YhE4iTPkhE}

 \video{Cloud}{19:46}{Part S (Updated)}{https://drive.google.com/open?id=1kgbrDiDNj0DKYi_ICvOXYeFZ32R1JH2_}
\slides{Cloud}{}{Part S (Updated)}{https://drive.google.com/open?id=1_LdE64DJqSKI7EmMbSsppHMO6KU4q4Sl}

 \video{Cloud}{11:29}{Part T (Updated)}{https://drive.google.com/open?id=1TQsCuR-2C6D_OJeJH818WO5-OBrA8Spo}
\slides{Cloud}{}{Part T (Updated)}{https://drive.google.com/open?id=1fVelFbLaUbNXMGS6ENRn4QHLzFitAyUD}

 \video{Cloud}{9:10}{Part U (Updated)}{https://drive.google.com/open?id=1jRpkdGCT-sQRb6pOGrW-qG58A_HYfr9W}
\slides{Cloud}{}{Part U (Updated)}{https://drive.google.com/open?id=1cR9YLcrtUMKINRFNMbdVre8Ydfa-lvAj}


\section{Retired lectures}

\video{Cloud}{8:31}{Introduction - (retired)}{https://www.youtube.com/watch?v=5lKj8_nqj9k}

\slides{Cloud}{Page 1}{Introduction - (retired)}{https://drive.google.com/open?id=1eXWtNlQ_jgeq_nVS_9B7MTaiDjzddXjC}

%\TODO{Information after after 4:56 is outdated.}

\section{Data Center Model}

A look at what truly defines a `cloud'. Advantages like scalability and
cost-effectiveness have promulgated commercial cloud offerings such as
Amazon EC2. Cloud architecture as divided into three layers:
Infrastructure as a Service, Platform as a Service, and Software as a
Service. AzureBlast is used as an example of how to utilize the cloud
setup. Certain misconceptions about clouds are then presented for
further discussion.

\video{Cloud}{8:08}{Data Center Model}{https://www.youtube.com/watch?v=6Hq_LuLB-RU}

\slides{Cloud}{Page 9}{Data Center Model}{https://drive.google.com/open?id=1eXWtNlQ_jgeq_nVS_9B7MTaiDjzddXjC}

\section{Data Intensive Sciences}

Some time is spent analyzing the current age of vast data growth, where
business, science, and consumer activity has seen an explosion of stored
data measured in exobytes. In response to this, the way we conduct
scientific research has also undergone an upgrade. However, the average
scientist would rather focus on their own research rather than spend
time trying to learn different methods of cloud and supercomputing.

\video{Cloud}{2:44}{Data Intensive Sciences}{https://www.youtube.com/watch?v=Ptoj3BME_z4}

\slides{Cloud}{Page 19}{Data Intensive Sciences}{https://drive.google.com/open?id=1eXWtNlQ_jgeq_nVS_9B7MTaiDjzddXjC}

\section{IaaS, PaaS and SaaS}

Definitions and examples are given for Infrastructure as a Service,
Platform as a Service, and Software as a Service. A chart is shown
illustrating how use of clouds trades cost and control for efficiency.
Following this is an exploration of the MapReduce program, and an
illustration of its concepts through WordCount. Finally, four distinct
approaches to MapReduce are compared.

\video{Cloud}{10:17}{IaaS/PaaS/SaaS}{https://www.youtube.com/watch?v=_irz3v1gT-A}

\slides{Cloud}{Page 25}{IaaS, PaaS and SaaS}{https://drive.google.com/open?id=1eXWtNlQ_jgeq_nVS_9B7MTaiDjzddXjC}

\section{Challenges}

The demands of Big Data calls for advances in areas like distributed
computing, systems management, internet technology, and hardware. Clouds
have become more prominent in the last few decades, so much so that many
people today take advantage of them without even knowing it. Of course,
this has also led to increased concerns about security, price, tech
support, etc. In spite of this, clouds still have clear advantages over
traditional computing models. A quiz is offered at the end asking
students to correctly place software in a hierarchy of computing.

\video{Cloud}{5:27}{Challenges}{https://www.youtube.com/watch?v=VpDRGcBe4s8}

\slides{Cloud}{Page 42}{Challenges}{https://drive.google.com/open?id=1eXWtNlQ_jgeq_nVS_9B7MTaiDjzddXjC}
