
##########

# Project Deliverables

## About delivering the project material

The project files, including the code and the report should be placed
in the Github repo of the leader of the team, while all the teammates
update their Readme files with the information about the project,
including the names of the teammates in the same order. All that are
not the leader must include the field: 

duplicate: yes 

in their project. You also must indicate if it is a project or report
in the type field

type: project

or

type: report 


While collaborating to the code,
the teammates can make pull requests to the repository of the leader,
which is the proper way to work on Github. However, if it’s necessary
for the other teammates to have writing access to the repo, they can
post to Piazza (mentioning the names and HIDs of the teammates), so
that the TAs will give them the privilege. Please do not share your
git account with other team members as we will chack if all team
members have contributed to the project. Team members that do not
contribute will not get any credit. Part of the class goal is to use
git properly.


## About reproducibility of the project

You are responsible for
providing clear and concise instructions on how to replicate your
project. If your code has a dependency on external libraries, you
might need to create a requirements file, Makefile, or just some bash
script that takes care of installing the dependencies and running your
project.

## About the project report

See the class requirements for the length and format of the
paper. Tables, figures, and algorithms/ code snippets are excluded
from the page count. Here is some suggestion for its structure:

2 pages to introduce your project in which you provide a title,
authors, abstract, keywords, hid, explain the problem, provide a
review, and motivate your solution for the problem.

2 pages for how you set up your solution, its architecture and
methods you use.

2 pages for results in which you evaluation of your solution, in terms
of performancem accuracy and compare it concretly to other work or
systems if avalable.

Your paper must be compilable with the Makefile. This is also mandated
for students using sharelatex. At one mpoint you need to install latex
locally on your machine and make sure your paper compiles without
errors. If you set up the paper in share latex exactly how you would
do it on your local computer, even share latex reports you the
errors. HOwever in the past we have seen that sharelatex produces a
PDF with errors and the students have ignored the errors produced by
share latex. Thus we make it mandatory that you check your paper locally.


success storries
https://piazza.com/class/j5wll7vzylg25j?cid=892

video
https://piazza.com/class/j5wll7vzylg25j?cid=679

NIST
https://piazza.com/class/j5wll7vzylg25j?cid=675


can be simplified as we no longer need to readd ```
https://github.com/bigdata-i523/hid231/blob/master/experiment/parse-readme/checkreadme.py



# DAL

http://sc17.supercomputing.org/2017/08/22/5863/

https://youtu.be/QymcdxZt4sM

################


sechi
https://piazza.com/class/j5wll7vzylg25j?cid=806
https://github.com/bigdata-i523/hid201/blob/master/experiment/Secchi%20Disk%20Data.ipynb


pi cluster
https://piazza.com/class/j5wll7vzylg25j?cid=150

bashrc
https://piazza.com/class/j5wll7vzylg25j?cid=147

virtualbox
https://piazza.com/class/j5wll7vzylg25j?cid=145

backups
https://piazza.com/class/j5wll7vzylg25j?cid=213

machines at iu
https://piazza.com/class/j5wll7vzylg25j?cid=212

article writing, not sure if useful
https://piazza.com/class/j5wll7vzylg25j?cid=203
https://piazza.com/class/j5wll7vzylg25j?cid=178

no windows 7
https://piazza.com/class/j5wll7vzylg25j?cid=192

vtx
https://piazza.com/class/j5wll7vzylg25j?cid=156
https://piazza.com/class/j5wll7vzylg25j?cid=246



old github
https://docs.google.com/document/d/1spfJdha1-9bb69tBgAGKGK2L0b8rb8wWJiY1r6VLKsc/edit

jabref video
https://piazza.com/class/j5wll7vzylg25j?cid=231

health care system cost
https://f100-res.cloudinary.com/image/upload/s--m6ebL-06--/c_fill,f_auto,g_faces,w_1200/v1/a/public/j7qglicviwcwfaofwgw7.jpg

connect to pi
https://piazza.com/class/j5wll7vzylg25j?cid=217
https://www.youtube.com/watch?v=gk7JAS5W7cE


experiments
https://piazza.com/class/j5wll7vzylg25j?cid=242
https://piazza.com/class/j5wll7vzylg25j?cid=241
https://piazza.com/class/j5wll7vzylg25j?cid=240
https://piazza.com/class/j5wll7vzylg25j?cid=239
https://piazza.com/class/j5wll7vzylg25j?cid=238

https://piazza.com/class/j5wll7vzylg25j?cid=237

https://piazza.com/class/j5wll7vzylg25j?cid=236
https://piazza.com/class/j5wll7vzylg25j?cid=235


# bibtex, latex:

code into latex: https://piazza.com/class/j5wll7vzylg25j?cid=846

https://piazza.com/class/j5wll7vzylg25j?cid=345
no use of names https://piazza.com/class/j5wll7vzylg25j?cid=312
no proposals: https://piazza.com/class/j5wll7vzylg25j?cid=434
sharelatex: https://piazza.com/class/j5wll7vzylg25j?cid=421
workbreakdown if working in teams
see https://cloudmesh.github.io/classes/i523/2017/project.html#common-deleiverable
we actually use em https://piazza.com/class/j5wll7vzylg25j?cid=405
page length https://piazza.com/class/j5wll7vzylg25j?cid=387
grammarly.com
videos: https://piazza.com/class/j5wll7vzylg25j?cid=359
latex ubuntu: https://piazza.com/class/j5wll7vzylg25j?cid=1021
https://www.tablesgenerator.com/
 print df.to_latex()
ref, label: https://piazza.com/class/j5wll7vzylg25j?cid=1065
turnitin.com
https://piazza.com/class/j5wll7vzylg25j?cid=603
https://piazza.com/class/j5wll7vzylg25j?cid=733
figure ref https://piazza.com/class/j5wll7vzylg25j?cid=759
no how published https://piazza.com/class/j5wll7vzylg25j?cid=769
https://piazza.com/class/j5wll7vzylg25j?cid=773


# Content of a paper

What should my paper include?

a) a statement and description of your chosen topic/problem

b) an explanation of how and why Big Data is involved in your
topic/problem

c) an explanation of how Big Data analytics and methods can help to
study your topic or solve the problem

d) an overview of what infrastructure, methods, etc. exist to perform
c), or how other people have tried to do

 
However, I feel that point (c) does not apply to my paper. I have
chosen the topic, Big Data Analytics using Spark. Since my paper
itself revolves around how big data analytics can be performed in an
efficient manner using Spark, I don't think that question (c) applies
to my topic. Please let me know if I am missing anything here.

Similarly, for point (d), I have included a comparison of Spark with
other frameworks like MapReduce to show how these two methods differ
when analyzing Big Data. However, I am not sure if that is what you
expect for point (d).

 



contributing
https://cloudmesh.github.io/classes/lesson/contrib/contributing.html

policy inactive students
https://piazza.com/class/j5wll7vzylg25j?cid=253

cmd5
https://piazza.com/class/j5wll7vzylg25j?cid=346
https://piazza.com/class/j5wll7vzylg25j?cid=337


pi
https://github.com/bigdata-i523/hid201/blob/master/python_stuff/raspberry_pi.md
https://github.com/seashiva94/cloudmesh.pi/blob/master/cloudmesh/pi/led_bar.py



piazza description exampel
https://piazza.com/iu/fall2017/i523/home?


some update tips (policy)

a) update notebook.md every week even if you have not done
anything. This is not much to ask as even if you were busy, I am sure
you can include a single entry in the notebook.md that you did not
have time. You can see the example in the Piazza resources link

 

b) In case you worked on the paper, you need to ckeck the updated
version into github. you can either work directly in githib, use
advanced commandline tools (some of you already know them, we will
explain them in the upcomming weeks) or paste and copy from sharelatex
or your local copy into the github repository.

 

c) If you work in teams it is up to you to identify a pathway so that
the verison in github is the one your team developed ofer that week.

 

d) We say: "mille viae ducunt homines per saecula Romam", which
translates to thousand roads lead men forever to Rome, and is these
days just refered to as All roads lead to Rome.

location in survey
https://piazza.com/class/j5wll7vzylg25j?cid=308


fork

https://piazza.com/class/j5wll7vzylg25j?cid=311

readme.yaml must be better dpcumented
https://piazza.com/class/j5wll7vzylg25j?cid=372

gregors mqtt
https://github.com/bigdata-i523/sample-hid000/tree/master/experiment/mqtt

pi project
https://piazza.com/class/j5wll7vzylg25j?cid=368
https://piazza.com/class/j5wll7vzylg25j?cid=547

yaml
use "if there is a : in the ext"
there is always a space after attribute :

piazza post hid 

plagiarizm: https://piazza.com/class/j5wll7vzylg25j?cid=503

miniproject
https://piazza.com/class/j5wll7vzylg25j?cid=526
https://piazza.com/class/j5wll7vzylg25j?cid=527
https://piazza.com/class/j5wll7vzylg25j?cid=528
https://piazza.com/class/j5wll7vzylg25j?cid=529
https://piazza.com/class/j5wll7vzylg25j?cid=530
https://piazza.com/class/j5wll7vzylg25j?cid=531
https://piazza.com/class/j5wll7vzylg25j?cid=532
https://piazza.com/class/j5wll7vzylg25j?cid=533

paper review
https://piazza.com/class/j5wll7vzylg25j?cid=536
what is good
what can be improved

slurm: https://piazza.com/class/j5wll7vzylg25j?cid=550

for gergor
https://piazza.com/class/j5wll7vzylg25j?cid=1018
https://piazza.com/class/j5wll7vzylg25j?cid=1056
CANVAS: https://piazza.com/class/j5wll7vzylg25j?cid=1057
CANVAS: https://piazza.com/class/j5wll7vzylg25j?cid=1058
https://piazza.com/class/j5wll7vzylg25j?cid=1070
https://piazza.com/class/j5wll7vzylg25j?cid=551
https://piazza.com/class/j5wll7vzylg25j?cid=601
https://piazza.com/class/j5wll7vzylg25j?cid=673
https://piazza.com/class/j5wll7vzylg25j?cid=717
https://piazza.com/class/j5wll7vzylg25j?cid=836
https://piazza.com/class/j5wll7vzylg25j?cid=861
https://piazza.com/class/j5wll7vzylg25j?cid=854

maps:
https://github.com/vgm64/gmplot
https://peak5390.wordpress.com/2012/12/08/matplotlib-basemap-tutorial-plotting-points-on-a-simple-map/

 histogram
https://piazza.com/class/j5wll7vzylg25j?cid=563
https://piazza.com/class/j5wll7vzylg25j?cid=564
https://piazza.com/class/j5wll7vzylg25j?cid=566
https://piazza.com/class/j5wll7vzylg25j?cid=572
https://piazza.com/class/j5wll7vzylg25j?cid=574

latex praise:
https://piazza.com/class/j5wll7vzylg25j?cid=600

python
wordcount
greyscale: https://piazza.com/class/j5wll7vzylg25j?cid=622
cmd5 projects:https://piazza.com/class/j5wll7vzylg25j?cid=644
https://piazza.com/class/j5wll7vzylg25j?cid=658
https://piazza.com/class/j5wll7vzylg25j?cid=780
https://piazza.com/class/j5wll7vzylg25j?cid=782
get data: https://piazza.com/class/j5wll7vzylg25j?cid=848
https://piazza.com/class/j5wll7vzylg25j?cid=886
https://piazza.com/class/j5wll7vzylg25j?cid=912

i do not recommend to use tkinter. maybe you can look at guizero or kivy. the other approach is to develop the gui side in javascript but have the backend in python

histogram
https://github.com/bigdata-i523/hid331/blob/master/experiment/jupyter/JupyterExperiment.ipynb

singularity
https://piazza.com/class/j5wll7vzylg25j?cid=656

jupyter
https://piazza.com/class/j5wll7vzylg25j?cid=657
https://piazza.com/class/j5wll7vzylg25j?cid=803

water
https://piazza.com/class/j5wll7vzylg25j?cid=704

assignments
https://piazza.com/class/j5wll7vzylg25j?cid=722

chameleon acess
https://piazza.com/class/j5wll7vzylg25j?cid=784

git
https://www.youtube.com/watch?v=WN0wGDfq57M&feature=youtu.be

ska lecture
https://piazza.com/class/j5wll7vzylg25j?cid=810

ethics and big data
https://piazza.com/class/j5wll7vzylg25j?cid=837

chameleon
resource limitation: https://piazza.com/class/j5wll7vzylg25j?cid=840

no tableu
https://piazza.com/class/j5wll7vzylg25j?cid=871

guizero
https://piazza.com/class/j5wll7vzylg25j?cid=875

cover page
https://piazza.com/class/j5wll7vzylg25j?cid=980

poll
https://piazza.com/class/j5wll7vzylg25j?cid=981

images 300dpi if not scalable

look at pinned discussons.

https://piazza.com/class/j5wll7vzylg25j?cid=694