\chapter{Assignments}

\section{Overview}
\FILENAME

We will post in this part all assignments for the various classes. As
this page will be updated frequently, it is in the students
responsibility to check.

It is in the
responsibility of the student to check this page and complete the
assignments. Some assignment may not be graded, but they still have to
be completed. To identify the assignment they carry the name of the
Lesson as well as a number. We try to alsoinclude a refernce to the
section where this assignment may be originating from.

The following are mandated assignments for this class

\section{Due Dates}

If not explicitly mentioned here the due dates are posted in Section
\ref{S:calendar}.

\section{Deliverables}

You will have graded assignments as documented in Section
{C:course-2018}. In addition we will post here some additional
assignments, some of which are pass/fail and are integrated in your
disccussion points. You will need to add them to your notebook and if
code is required to include an explicit URL to where that particular
code is in your git repository.

\section{Week 1}

\begin{itemize}\renewcommand{\labelitemi}{\scriptsize$\square$}
\item  Watch the introduction video at:
  \url{https://youtu.be/yC3PNkb_9mI}

\item Exercise~\ref{E:Piazza.1} in Chapter \nameref{C:piazza} on page \pageref{E:Piazza.1}
\item Exercise~\ref{E:Piazza.2} in Chapter \nameref{C:piazza} on page \pageref{E:Piazza.2}
\item Exercise~\ref{E:Piazza.3} in Chapter \nameref{C:piazza} on page \pageref{E:Piazza.3}
\item Exercise~\ref{E:Documentation.1} on page \pageref{E:Documentation.1}

\item Exercise.Organization.1 e-organization
\item Exercise.Organization.2 e-organization
\item Exercise.Organization.3 e-organization
\item Exercise.Organization.4 e-organization
\item Exercise.Organization.5 e-organization
\item 
  Conduct the entry survey after you have done the above assignments:
  \TODO{Old link:
  \url{https://piazza.com/class/j5wll7vzylg25j?cid=67}, new links will
be different for class}

\item 
  Learn about Piazza folders:
  \TODO{old link:
  \url{https://piazza.com/class/j5wll7vzylg25j?cid=103}, new links
  will be different for class}
\end{itemize}

Optional Assignment:

\begin{itemize}
\item Buy Hardware for IoT
\TODO{e616 will have hardware
  \url{https://piazza.com/class/j5wll7vzylg25j?cid=55}}
\end{itemize}

Complete the above within the first week!

\begin{comment}
\section{Week 2}\label{week-2}

This may take multiple weeks to complete for some of you:

Learn on how to use piazza for the class

\begin{itemize}
\item Exercise.Piazza.4 e-piazza
\end{itemize}

Learn Python

\begin{itemize}
\item Exercise.Python.1 e-python
\end{itemize}

\begin{description}
\item[Paper 1 Topic:]
Identify the topic for your individual paper 1 and post it on Piazza:
\url{https://piazza.com/class/j5wll7vzylg25j?cid=158} . The paper will
be due on Oct 9, 9am.
\end{description}

\section{Week 3}\label{week-3}

This assignment may take some of you multiple weeks.

Implement a command using

\begin{itemize}

\item
 Exercise.CMD5.2 e-cmd5
\end{itemize}

that is called ``hello'' that prints hello world. Use docopts to define
the command.

Use cms sys generate command hello

There will be a tutorial about this.

Learning about Git pull Requests while using the Class web page as
example. Only make small changes based on a paragraph and create a pull
request for it.

\begin{itemize}

\item
 Exercise.Contrib.0 e-contrib
\item
 Exercise.Contrib.1 e-contrib
\item
 Exercise.Contrib.5 e-contrib
\end{itemize}

There will be tutorials about this

\begin{description}
\item[Polls]
Please fill out the following polls on Piazza. They will used to track
your progress:

\begin{itemize}

\item
  Who has or will have a Raspberry Pi or esp8266?
  \url{https://piazza.com/class/j5wll7vzylg25j?cid=182}
\item
  Where do you intend to program in python?
  \url{https://piazza.com/class/j5wll7vzylg25j?cid=183}
\item
  What is your python knowledge?
  \url{https://piazza.com/class/j5wll7vzylg25j?cid=184}
\item
  Which lectures did you view?
  \url{https://piazza.com/class/j5wll7vzylg25j?cid=185}
\end{itemize}
\end{description}

\section{Week 4}\label{week-4}

Please identify your paper 2 topic immediately. Post it in the Followup
Discussion section of this Piazza post with the specified format:
\url{https://piazza.com/class/j5wll7vzylg25j?cid=187}

\section{Week 5}\label{week-5}

\begin{itemize}
\item
  Please read the following post on Piazza and make sure your README.md
  file is up to date (Deadline: Friday 22 Sept 9am):
  \url{https://piazza.com/class/j5wll7vzylg25j?cid=252}
\item
  \begin{description}
  \item[Experiments]
  A number of experiments are posted on Piazza. They are not
  assignments, but are experiments and if you do them right, they will
  lead to material that can be shared with all students. Experiments can
  lead to discussion points that go into your discussion grade. Here are
  the links:

  \begin{itemize}

  \item
    Description \url{https://piazza.com/class/j5wll7vzylg25j?cid=240}
  \item
   Exercise.: Experimenting with gitbash on windows
    \url{https://piazza.com/class/j5wll7vzylg25j?cid=236}
  \item
   Exercise.: Experimenting Windows Subsystem for Linux Documentation
    \url{https://piazza.com/class/j5wll7vzylg25j?cid=237}
  \item
   Exercise.: Experimenting with MQTT
    \url{https://piazza.com/class/j5wll7vzylg25j?cid=238}
  \item
   Exercise.: Experimenting with Graphs
    \url{https://piazza.com/class/j5wll7vzylg25j?cid=239}
  \item
   Exercise.: Experimenting with IoT sculptures
    \url{https://piazza.com/class/j5wll7vzylg25j?cid=241}
  \item
   Exercise.: Build a camera enhanced Raspberry Pi robot car
    \url{https://piazza.com/class/j5wll7vzylg25j?cid=242}
  \item
    Exercise: Build a Raspberry PI docker swarm cluster
    \url{https://piazza.com/class/j5wll7vzylg25j?cid=243}
  \end{itemize}
  \end{description}
\end{itemize}

\section{Week 6}\label{week-6}

Group activity for Residential Students

Work on one of the following discussion posts on Piazza. You will work
in groups that were formed in the class on Friday Sep 25. Post the
results of your work on Piazza by next Thursday (Oct 5) 11:59 PM

\begin{itemize}

\item
  Python 2 vs 3 \url{https://piazza.com/class/j5wll7vzylg25j?cid=333}
\item
  Data formats \url{https://piazza.com/class/j5wll7vzylg25j?cid=334}
\item
  Cloudmesh.cmd5 \url{https://piazza.com/class/j5wll7vzylg25j?cid=335}
\item
  Raspberry Pi \url{https://piazza.com/class/j5wll7vzylg25j?cid=336}
\item
  open: cloudmesh.cmd5 on Windows Native and with docker
  \url{https://piazza.com/class/j5wll7vzylg25j?cid=337}
\item
  open: MQTT \url{https://piazza.com/class/j5wll7vzylg25j?cid=338}
    
\end{itemize}

\end{comment}