

\section{Assignments}\label{assignments}

\FILENAME\

Lessons may include a number of Exercises. However you do not have to do
all of them. We list hire all defined assignments for this class and
will add to this page throughout the semester. It is in the
responsibility of the student to check this page and complete the
assignments. Some assignment may not be graded, but they still have to
be completed. To identify the assignment they carry the name of the
Lesson as well as a number.

The following are mandated assignments for this class

\subsection{Week 1}\label{week-1}

Using Piazza

\begin{itemize}

\item
  Watch the introduction video at: \url{https://youtu.be/yC3PNkb_9mI}
\item
  EPiazza.1 e-piazza
\item
  EPiazza.2 e-piazza
\item
  EPiazza.3 e-piazza
\item
  EOrganization.1 e-organization
\item
  EOrganization.2 e-organization
\item
  EOrganization.3 e-organization
\item
  EOrganization.4 e-organization
\item
  EOrganization.5 e-organization
\item
  Conduct the entry survey after you have done the above assignments:
  \url{https://piazza.com/class/j5wll7vzylg25j?cid=67}
\item
  Learn about Piazza folders:
  \url{https://piazza.com/class/j5wll7vzylg25j?cid=103}
\end{itemize}

Optional Assignment:

\begin{itemize}

\item
  Buy Hardware for IoT
  \url{https://piazza.com/class/j5wll7vzylg25j?cid=55}
\end{itemize}

\begin{description}
\item[How do you find the assignments?:]
go to the class web page and search for the string EOrganization or
EPiazza. A web link will sho up that contains a section where you can
find details about the assignment.

Alternatively click on the Exercise link, gets you there faster \ldots{}
\end{description}

Complete the above within the first week!

\subsection{Week 2}\label{week-2}

This may take multiple weeks to complete for some of you:

Learn on how to use piazza for the class

\begin{itemize}

\item
  EPiazza.4 e-piazza
\end{itemize}

Learn Python

\begin{itemize}

\item
  EPython.1 e-python
\end{itemize}

\begin{description}
\item[Paper 1 Topic:]
Identify the topic for your individual paper 1 and post it on Piazza:
\url{https://piazza.com/class/j5wll7vzylg25j?cid=158} . The paper will
be due on Oct 9, 9am.
\end{description}

\subsection{Week 3}\label{week-3}

This assignment may take some of you multiple weeks.

Implement a command using

\begin{itemize}

\item
  ECMD5.2 e-cmd5
\end{itemize}

that is called ``hello'' that prints hello world. Use docopts to define
the command.

Use cms sys generate command hello

There will be a tutorial about this.

Learning about Git pull Requests while using the Class web page as
example. Only make small changes based on a paragraph and create a pull
request for it.

\begin{itemize}

\item
  EContrib.0 e-contrib
\item
  EContrib.1 e-contrib
\item
  EContrib.5 e-contrib
\end{itemize}

There will be tutorials about this

\begin{description}
\item[Polls]
Please fill out the following polls on Piazza. They will used to track
your progress:

\begin{itemize}

\item
  Who has or will have a Raspberry Pi or esp8266?
  \url{https://piazza.com/class/j5wll7vzylg25j?cid=182}
\item
  Where do you intend to program in python?
  \url{https://piazza.com/class/j5wll7vzylg25j?cid=183}
\item
  What is your python knowledge?
  \url{https://piazza.com/class/j5wll7vzylg25j?cid=184}
\item
  Which lectures did you view?
  \url{https://piazza.com/class/j5wll7vzylg25j?cid=185}
\end{itemize}
\end{description}

\subsection{Week 4}\label{week-4}

Please identify your paper 2 topic immediately. Post it in the Followup
Discussion section of this Piazza post with the specified format:
\url{https://piazza.com/class/j5wll7vzylg25j?cid=187}

\subsection{Week 5}\label{week-5}

\begin{itemize}
\item
  Please read the following post on Piazza and make sure your README.md
  file is up to date (Deadline: Friday 22 Sept 9am):
  \url{https://piazza.com/class/j5wll7vzylg25j?cid=252}
\item
  \begin{description}
  \item[Experiments]
  A number of experiments are posted on Piazza. They are not
  assignments, but are experiments and if you do them right, they will
  lead to material that can be shared with all students. Experiments can
  lead to discussion points that go into your discussion grade. Here are
  the links:

  \begin{itemize}

  \item
    Description \url{https://piazza.com/class/j5wll7vzylg25j?cid=240}
  \item
    E: Experimenting with gitbash on windows
    \url{https://piazza.com/class/j5wll7vzylg25j?cid=236}
  \item
    E: Experimenting Windows Subsystem for Linux Documentation
    \url{https://piazza.com/class/j5wll7vzylg25j?cid=237}
  \item
    E: Experimenting with MQTT
    \url{https://piazza.com/class/j5wll7vzylg25j?cid=238}
  \item
    E: Experimenting with Graphs
    \url{https://piazza.com/class/j5wll7vzylg25j?cid=239}
  \item
    E: Experimenting with IoT sculptures
    \url{https://piazza.com/class/j5wll7vzylg25j?cid=241}
  \item
    E: Build a camera enhanced Raspberry Pi robot car
    \url{https://piazza.com/class/j5wll7vzylg25j?cid=242}
  \item
    E: Build a Raspberry PI docker swarm cluster
    \url{https://piazza.com/class/j5wll7vzylg25j?cid=243}
  \end{itemize}
  \end{description}
\end{itemize}

\subsection{Week 6}\label{week-6}

Group activity for Residential Students

Work on one of the following discussion posts on Piazza. You will work
in groups that were formed in the class on Friday Sep 25. Post the
results of your work on Piazza by next Thursday (Oct 5) 11:59 PM

\begin{itemize}

\item
  Python 2 vs 3 \url{https://piazza.com/class/j5wll7vzylg25j?cid=333}
\item
  Data formats \url{https://piazza.com/class/j5wll7vzylg25j?cid=334}
\item
  Cloudmesh.cmd5 \url{https://piazza.com/class/j5wll7vzylg25j?cid=335}
\item
  Raspberry Pi \url{https://piazza.com/class/j5wll7vzylg25j?cid=336}
\item
  open: cloudmesh.cmd5 on Windows Native and with docker
  \url{https://piazza.com/class/j5wll7vzylg25j?cid=337}
\item
  open: MQTT \url{https://piazza.com/class/j5wll7vzylg25j?cid=338}
    
\end{itemize}
