\section{Authors}

\FILENAME

\begin{description}

\item[Gregor von Laszewski] \index{von Laszewski, Gregor} Gregor von
  Laszewski is an Assistant Director DSC in the School of Informatics
  and Computing and Engeneering at Indiana University. He holds also a
  position as Adjunct Professor in the Intelligent Systems Engineering
  Department. Previously he held Adjunct Professor positions at the
  Computer Science Department at Indiana University and University of
  North Texas. He received a Ph.D. from Syracuse University in
  computer science.

  He served as the architect of the the FutureGrid project. He held a
  position at Argonne National Laboratory where he was last a
  scientist and a fellow of the Computationand part of the initial
  team working on Grid computing.

  At IU He served as the architect of the the FutureGrid project. His
  current interest and projects include cloud computing, big data, and
  scientific impact metrics, and edge computing.  He initiated the
  Cloudmesh project which is a toolkit to enable cloud computing
  across various Cloud and Container IaaS such as OpenStack, AWS,
  Azure, docker, docker swarm, and kubernetes.


\item[Geoffrey C. Fox] \index{Fox, Geoffrey C} Fox received a Ph.D. in
  Theoretical Physics from Cambridge University and is now
  distinguished professor of Informatics and Computing, and Physics at
  Indiana University where he is director of the Digital Science
  Center, Chair of Department of Intelligent Systems Engineering and
  Director of the Data Science program at the School of Informatics,
  Computing, and Engineering.

  He currently works in applying computer science from infrastructure
  to analytics in Biology, Pathology, Sensor Clouds, Earthquake and
  Ice-sheet Science, Image processing, Deep Learning, Manufacturing,
  Network Science and Particle Physics. The infrastructure work is
  built around Software Defined Systems on Clouds and Clusters. The
  analytics focuses on scalable parallelism.

\item [Dr. Judy Qiu] is an Associate Professor in the School of
  Informatics and Computing at Indiana University. Her research
  interests focus on data-intensive computing at the intersection of
  cloud and multicore technologies, with an emphasis on life science
  applications using MapReduce as well as traditional parallel and
  distributed computing approaches. Her contributions are focused on
  Hadoop and Introdcution into Cloud Computing. 

\end{description}

\section{Acknowledgements}

Part \ref{P:chameleon} focussing on Chameleon Cloud was contributed by
Kate Kaheay the lead of the Chameleon Cloud project sponsored by NSF
grant 1743358, Collaborative Research: Chameleon: A Large-Scale,
Reconfigurable Experimental Environment for Cloud Research. Some
content has been modified and added by Gregor von Laszewski to target
specifically classes and education material targeted for Indiana
University.
