% chktex-file 1


\chapter{Exercises}
\FILENAME\

\section{Docker Swarm Tutorial}

\begin{exercise}

  Develop a tutorial that deploys a Docker Swarm cluster on a number
  of ubuntu machines. Note that this may actually be easier as docker
  and docker swarm are distributed with recent versions of
  ubuntu. Just in case we are providing a link to an effort we found
  to install docker swarm. However we have not checked it or
  identified if it is useful.
 
  \URL{https://rominirani.com/docker-swarm-tutorial-b67470cf8872}

\end{exercise}


\section{Docker Swarm on Google Compute Engine}

\begin{exercise}
  Develop a tutorial that deploys a Docker Swarm cluster on Google
  Compute Engine. Note that this may actually be easier as docker
  and docker swarm are distributed with recent versions of
  ubuntu. Just in case we are providing a link to an effort we found
  to install docker swarm. However we have not checked it or
  identified if it is useful.

  \URL{https://rominirani.com/docker-swarm-on-google-compute-engine-364765b400ed}

\end{exercise}

\section{Single Node Hadoop}

\begin{exercise}

At

\url{https://hadoop.apache.org/docs/current/hadoop-project-dist/hadoop-common/SingleCluster.html}

you will find a comprehensive installation instruction that sets up a
hadoop cluster on a single node. 

(a) Create a Dockerfile that deploys hadoop in a container

(b) Develop sample applications and tests to test your cluster. You
can use wordcount or similar.

\end{exercise}


\section{Single Node Hadoop}

\begin{exercise}

At

\url{https://hadoop.apache.org/docs/r3.0.0/hadoop-project-dist/hadoop-common/ClusterSetup.html}

you will find a comprehensive installation instruction that sets up a
hadoop cluster in a distributed environment, can you use this set of
instructions aor identify other resources on the internet that allow
the creation of a hadoop cluster on kubernetes. You can use docker
compose for this.


(a) Create docker compose and Dockerfiles that deploys hadoop in
kubernetes

(b) Develop sample applications and tests to test your cluster. You
can use wordcount or similar.

\end{exercise}



\section{Spark Cluster}

\begin{exercise}

Develop a high quality tutorial that installes a spark cluster in
kubernetes. Test your deployment on minikube but also Futuresystems
echo.

You may want to get inspired from the talk \textit{Scalable Spark
  Deployment using Kubernetes}:

\URL{http://blog.madhukaraphatak.com/scaling-spark-with-kubernetes-part-1/}
\URL{http://blog.madhukaraphatak.com/scaling-spark-with-kubernetes-part-2/}
\URL{http://blog.madhukaraphatak.com/scaling-spark-with-kubernetes-part-3/}
\URL{http://blog.madhukaraphatak.com/scaling-spark-with-kubernetes-part-4/}
\URL{http://blog.madhukaraphatak.com/scaling-spark-with-kubernetes-part-5/}
\URL{http://blog.madhukaraphatak.com/scaling-spark-with-kubernetes-part-6/}
\URL{http://blog.madhukaraphatak.com/scaling-spark-with-kubernetes-part-7/}
\URL{http://blog.madhukaraphatak.com/scaling-spark-with-kubernetes-part-8/}
\URL{http://blog.madhukaraphatak.com/scaling-spark-with-kubernetes-part-9/}

Make sure you do not plagiarize.

\end{exercise}