% chktex-file 1

\chapter{Draft: Container}

\FILENAME




\section{Container Orchestration Tools: Compare Kubernetes vs Docker Swarm}

\URL{https://platform9.com/blog/compare-kubernetes-vs-docker-swarm/}

\section{Gentle introduction to Containers}

\URL{https://www.slideshare.net/jpetazzo/introduction-docker-linux-containers-lxc}

\section{Tutorialspoint}

\URL{https://www.tutorialspoint.com/docker/index.htm}

\URL{https://www.tutorialspoint.com/docker/docker_tutorial.pdf}

\URL{https://www.tutorialspoint.com/docker/docker_pdf_version.htm}


\chapter{Exercises}

\section{Docker Swarm Tutorial}

\begin{exercise}

  Develop a tutorial that deploys a Docker Swarm cluster on a number
  of ubuntu machines. Note that this may actually be easier as docker
  and docker swarm are distributed with recent versions of
  ubuntu. Just in case we are providing a link to an effort we found
  to install docker swarm. However we have not checked it or
  identified if it is useful.
 
  \URL{https://rominirani.com/docker-swarm-tutorial-b67470cf8872}

\end{exercise}


\section{Docker Swarm on Google Compute Engine}

\begin{exercise}
  Develop a tutorial that deploys a Docker Swarm cluster on Google
  Compute Engine. Note that this may actually be easier as docker
  and docker swarm are distributed with recent versions of
  ubuntu. Just in case we are providing a link to an effort we found
  to install docker swarm. However we have not checked it or
  identified if it is useful.

  \URL{https://rominirani.com/docker-swarm-on-google-compute-engine-364765b400ed}

\end{exercise}

\section{Spark Cluster}

\begin{exercise}

Develop a high quality tutorial that installes a spark cluster in
kubernetes. Test your deployment on minikube but also Futuresystems
echo.

You may want to get inspired from the talk \textit{Scalable Spark
  Deployment using Kubernetes}:

\URL{http://blog.madhukaraphatak.com/scaling-spark-with-kubernetes-part-1/}
\URL{http://blog.madhukaraphatak.com/scaling-spark-with-kubernetes-part-2/}
\URL{http://blog.madhukaraphatak.com/scaling-spark-with-kubernetes-part-3/}
\URL{http://blog.madhukaraphatak.com/scaling-spark-with-kubernetes-part-4/}
\URL{http://blog.madhukaraphatak.com/scaling-spark-with-kubernetes-part-5/}
\URL{http://blog.madhukaraphatak.com/scaling-spark-with-kubernetes-part-6/}
\URL{http://blog.madhukaraphatak.com/scaling-spark-with-kubernetes-part-7/}
\URL{http://blog.madhukaraphatak.com/scaling-spark-with-kubernetes-part-8/}
\URL{http://blog.madhukaraphatak.com/scaling-spark-with-kubernetes-part-9/}

Make sure you do not plagiarize.

\end{exercise}