
\chapter{Sports}
\label{c:sports}
\index{Sports}

\FILENAME\

Sports sees significant growth in analytics with pervasive statistics
shifting to more sophisticated measures. We start with baseball as game
is built around segments dominated by individuals where detailed
(video/image) achievement measures including PITCHf/x and FIELDf/x are
moving field into big data arena. There are interesting relationships
between the economics of sports and big data analytics. We look at
Wearables and consumer sports/recreation. The importance of spatial
visualization is discussed. We look at other Sports: Soccer, Olympics,
NFL Football, Basketball, Tennis and Horse Racing.

\section{Basic Sabermetrics}

This unit discusses baseball starting with the movie Moneyball and the
2002-2003 Oakland Athletics. Unlike sports like basketball and soccer,
most baseball action is built around individuals often interacting in
pairs. This is much easier to quantify than many player phenomena in
other sports. We discuss Performance-Dollar relationship including new
stadiums and media/advertising. We look at classic baseball averages and
sophisticated measures like Wins Above Replacement.


\slides{Sport}{40}{Overview}{https://drive.google.com/open?id=0B8936_ytjfjmbWt6bGZuTFJ4TFE}


\subsection{Introduction and Sabermetrics (Baseball Informatics)
  Lesson}

Introduction to all Sports Informatics, Moneyball The 2002-2003 Oakland
Athletics, Diamond Dollars economic model of baseball, Performance -
Dollar relationship, Value of a Win.


\video{Sport}{31:4}{Introduction and Sabermetrics (Baseball Informatics) Lesson}{https://www.youtube.com/watch?v=Dd4zV__G5Q8} 


\subsection{Basic Sabermetrics}\label{basic-sabermetrics}

Different Types of Baseball Data, Sabermetrics, Overview of all data,
Details of some statistics based on basic data, OPS, wOBA, ERA, ERC,
FIP, UZR.


\video{Sport}{26:53}{Basic Sabermetrics}{https://www.youtube.com/watch?v=L0X-RQJZKrs} 



\subsection{Wins Above Replacement}\label{wins-above-replacement}

Wins above Replacement WAR, Discussion of Calculation, Examples,
Comparisons of different methods, Coefficient of Determination, Another,
Sabermetrics Example, Summary of Sabermetrics.


\video{Sport}{30:43}{Wins Above Replacement}{https://www.youtube.com/watch?v=D6PHqPor4LA} 




\section{Advanced  Sabermetrics}\label{sports-informatics-ii-sabermetrics-advanced}

This unit discusses `advanced sabermetrics' covering advances possible
from using video from PITCHf/X, FIELDf/X, HITf/X, COMMANDf/X and MLBAM.


\slides{Sport}{41}{Sporta II}{https://drive.google.com/open?id=0B8936_ytjfjmUDh0Y01GbW9tWnc}


\subsection{Pitching Clustering}\label{pitching-clustering}

A Big Data Pitcher Clustering method introduced by Vince Gennaro, Data
from Blog and video at 2013 SABR conference.


\video{Sport}{20:59}{Pitching Clustering}{https://www.youtube.com/watch?v=rZ9-b54aEvw} 


\subsection{Pitcher Quality}\label{pitcher-quality}

Results of optimizing match ups, Data from video at 2013 SABR
conference.


\video{Sport}{10:02}{Pitcher Quality}{https://www.youtube.com/watch?v=OkkUaySvXOY} 



\section{PITCHf/X}\label{pitchfx}

Examples of use of PITCHf/X.


\video{Sport}{10:39}{PITCHf/X}{https://www.youtube.com/watch?v=m7IXhsHgQmE} 


\subsection{Other Video Data Gathering in Baseball}

FIELDf/X, MLBAM, HITf/X, COMMANDf/X.


\video{Sport}{18:5}{Other Video Data Gathering in Baseball}{https://www.youtube.com/watch?v=nKZiOOGccms}



\section{Other Sports}

We look at Wearables and consumer sports/recreation. The importance of
spatial visualization is discussed. We look at other Sports: Soccer,
Olympics, NFL Football, Basketball, Tennis and Horse Racing.


\slides{Sport}{Sports III}{44}{https://drive.google.com/open?id=0B8936_ytjfjmUGdpUzFaRzhyWXM}


\subsection{Wearables}\label{wearables}

Consumer Sports, Stake Holders, and Multiple Factors.


\video{Sport}{22:2}{Wearables}{https://www.youtube.com/watch?v=F_cPq6xIXw0} 


\subsection{Soccer and the Olympics}\label{soccer-and-the-olympics}

Soccer, Tracking Players and Balls, Olympics.


\video{Sport}{8:28}{Soccer and the Olympics}{https://www.youtube.com/watch?v=AiZneaLJMTs} 



\subsection{Spatial Visualization in NFL and NBA}

NFL, NBA, and Spatial Visualization.


\video{Sport}{15:19}{Spatial Visualization in NFL and NBA}{https://www.youtube.com/watch?v=Uorh3RJLC1s}


\subsection{Tennis and Horse Racing}

Tennis, Horse Racing, and Continued Emphasis on Spatial Visualization.


\video{Sport}{8:52}{Tennis and Horse Racing}{https://www.youtube.com/watch?v=2P-pismFSrI}  

\subsection{Resources}

\TODO{These resources have not all been checked to see if they still
  exist this is curretnly in progress}


\begin{itemize}
\item
  \url{http://www.sloansportsconference.com/?page_id=481\&sort_cate=Research\%20Paper}
\item
  \url{http://www.slideshare.net/Tricon_Infotech/big-data-for-big-sports}
\item
  \url{http://www.slideshare.net/BrandEmotivity/sports-analytics-innovation-summit-data-powered-storytelling}
\item
  \url{http://www.liveathos.com/apparel/app}
\item
  \url{http://www.slideshare.net/elew/sport-analytics-innovation}
\item
  \url{http://www.wired.com/2013/02/catapault-smartball/}
\item
  \url{http://www.sloansportsconference.com/wp-content/uploads/2014/06/Automated_Playbook_Generation.pdf}
\item
  \url{http://autoscout.adsc.illinois.edu/publications/football-trajectory-dataset/}
\item
  \url{http://www.sloansportsconference.com/wp-content/uploads/2012/02/Goldsberry_Sloan_Submission.pdf}
\item
  \url{http://gamesetmap.com/}
\item
  \url{http://www.trakus.com/technology.asp\#tNetText}
\end{itemize}


\begin{itemize}
\item
  \url{http://www.slideshare.net/BrandEmotivity/sports-analytics-innovation-summit-data-powered-storytelling}
\item
  \url{http://www.sloansportsconference.com/}
\item
  \url{http://sabr.org/}
\item
  \url{http://en.wikipedia.org/wiki/Sabermetrics}
\item
  \url{http://en.wikipedia.org/wiki/Baseball_statistics}
\item
  \url{http://www.sportvision.com/baseball}
\item
  \url{http://m.mlb.com/news/article/68514514/mlbam-introduces-new-way-to-analyze-every-play}
\item
  \url{http://www.fangraphs.com/library/offense/offensive-statistics-list/}
\item
  \url{http://en.wikipedia.org/wiki/Component_ERA}
\item
  \url{http://www.fangraphs.com/library/pitching/fip/}
\item
  \url{http://nomaas.org/2012/05/a-look-at-the-defense-the-yankees-d-stinks-edition/}
\item
  \url{http://en.wikipedia.org/wiki/Wins_Above_Replacement}
\item
  \url{http://www.fangraphs.com/library/misc/war/}
\item
  \url{http://www.baseball-reference.com/about/war_explained.shtml}
\item
  \url{http://www.baseball-reference.com/about/war_explained_comparison.shtml}
\item
  \url{http://www.baseball-reference.com/about/war_explained_position.shtml}
\item
  \url{http://www.baseball-reference.com/about/war_explained_pitch.shtml}
\item
  \url{http://www.fangraphs.com/leaders.aspx?pos=all\&stats=bat\&lg=all\&qual=y\&type=8\&season=2014\&month=0\&season1=1871\&ind=0}
\item
  \url{http://battingleadoff.com/2014/01/08/comparing-the-three-war-measures-part-ii/}
\item
  \url{http://battingleadoff.com/2014/01/08/comparing-the-three-war-measures-part-ii/}
\item
  \url{http://en.wikipedia.org/wiki/Coefficient_of_determination}
\item
  \url{http://www.sloansportsconference.com/wp-content/uploads/2014/02/2014_SSAC_Data-driven-Method-for-In-game-Decision-Making.pdf}
\item
  \url{https://courses.edx.org/courses/BUx/SABR101x/2T2014/courseware/10e616fc7649469ab4457ae18df92b20/}
\end{itemize}


\begin{itemize}
\item
  \url{http://vincegennaro.mlblogs.com/}
\item
  \url{https://www.youtube.com/watch?v=H-kx-x_d0Mk}
\item
  \url{http://www.sportvision.com/media/pitchfx-how-it-works}
\item
  \url{http://www.baseballprospectus.com/article.php?articleid=13109}
\item
  \url{http://baseball.physics.illinois.edu/FastPFXGuide.pdf}
\item
  \url{http://baseball.physics.illinois.edu/FieldFX-TDR-GregR.pdf}
\item
  \url{http://www.sportvision.com/baseball/fieldfx}
\item
  \url{http://regressing.deadspin.com/mlb-announces-revolutionary-new-fielding-tracking-syste-1534200504}
\item
  \url{http://grantland.com/the-triangle/mlb-advanced-media-play-tracking-bob-bowman-interview/}
\item
  \url{http://www.sportvision.com/baseball/hitfx}
\item
  \url{https://www.youtube.com/watch?v=YkjtnuNmK74}
\end{itemize}
