\section{Introduction to Hadoop}
\label{c:spark}
\FILENAME\

Hadoop is an open source framework for storage and processing of large
datasets on commodity clusters. Hadoop internally uses its own file
system called HDFS (Hadoop Distributed File System).

\subsection{Motivation-Hadoop}
\label{s:motivation-spark}

In this section we discuss about the background of Mapreduce along with Hadoop and
core components of Hadoop.
\TODO{Gregor: Update Video Hadoop Urls to Youtube Urls}
\video{Hadoop}{19:02}{Hadoop
  A}{https://drive.google.com/file/d/1CmtoDDio-CYT9g4bsjclVfukA5TsIc8n/view?usp=sharing}

\subsection{Hadoop-MapReduce}

In this section we discuss about the usage Hadoop MapReduce architecture.
\TODO{Gregor: Update Video Hadoop Urls to Youtube Urls}
\video{Hadoop}{13:19}{Hadoop
  B}{https://drive.google.com/file/d/1ppMW0LRJFGYlDyFhBIi8PNaHG2SEx-WU/view?usp=sharing}

\subsection{Hadoop-EcoSystem}

In this section we discuss about the Hadoop EcoSystem and the architecture. 
\TODO{Gregor: Update Video Hadoop Urls to Youtube Urls}
\video{Hadoop}{12:57}{Hadoop
  C}{https://drive.google.com/file/d/1UPJRNgPCRqhhAUdBViPvTT1TwcRy4hp9/view?usp=sharing}

\subsection{Hadoop-Components}

In this section we discuss about Hadoop Components in detail.
\TODO{Gregor: Update Video Hadoop Urls to Youtube Urls}
\video{Hadoop}{15:14}{Hadoop
  D}{https://drive.google.com/file/d/14YrWVgK8qlJ6h53pwck7dSovoDYZEnkn/view?usp=sharing}


\subsection{Hadoop-Yarn Resource Manager}

In this section we discuss about Yarn resource manager and novel components added to the
Hadoop framework in case of improving the performance and minimizing fault tolerance. 
\TODO{Gregor: Update Video Hadoop Urls to Youtube Urls}
\video{Hadoop}{14:55}{Hadoop
  E}{https://drive.google.com/file/d/1WbcwbGVXb2kJJ1uSxkgcOarh72cVh_VE/view?usp=sharing}

\subsection{PageRank}

In this section we discuss about a real world problem that can be solved using the MapReduce
technique. PageRank is a problem solved by the earliest stages of the Google.inc. In this
section we discuss about the theoretical background about this problem and we discuss how this
can be solved using the map reduce concepts.
\TODO{Gregor: Update Video Hadoop Urls to Youtube Urls}
\video{Hadoop}{15:14}{Hadoop
  E}{https://drive.google.com/file/d/1k8RHHY8cwgIN7HcoBQyhaSEhuIbWl-Qw/view?usp=sharing}

