\section{Twister2 Installation}\label{s:twister2-installation}

\subsection{Prerequisites}

\begin{itemize}
\item Operating Systems = [Red Hat Enterprise Linux Server release 7, Ubuntu 14.04 , Ubuntu 16.04] \verb|We only use Ubuntu 16.04|
\item Java (Jdk 1.8) Covered in Section \ref{s:hadoop-local-installation}.
\item G++ Compiler \verb|sudo apt-get install g++|
\item Maven Installation Explained in Section\ref{s:s:twister2-maven}
\item OpenMPI Installation Explained in Section\ref{s:s:twister2-openmpi}
\item Bazel Build Installation Explained in Section\ref{s:s:twister2-bazel}
\item Additional Libraries Explained in Section\ref{s:s:twister2-extras}
\end{itemize}

\subsubsection{Maven Installation}\label{s:s:twister2-maven}

Execute the following commands to install Maven locally. 

\begin{lstlisting}
  mkdir -p ~/cloudmesh/bin/maven
  cd ~/cloudmesh/bin/maven
  wget http://mirrors.ibiblio.org/apache/maven/maven-3/3.5.2/binaries/apache-maven-3.5.2-bin.tar.gz
  tar xzf apache-maven-3.5.2-bin.tar.gz  
\end{lstlisting}

Adding environmental variables

\begin{lstlisting}
  emacs ~/.bashrc  
\end{lstlisting}

Add the following line at the end of the file.

\begin{lstlisting}
  MAVEN_HOME=~/cloudmesh/bin/maven/apache-maven-3.5.2
  PATH=$MAVEN_HOME/bin:$PATH
  export MAVEN_HOME PATH
\end{lstlisting}

\begin{lstlisting}
  source ~/.bashrc
\end{lstlisting}

\subsubsection{OpenMPI Installation}\label{s:s:twister2-openmpi}

For Twister2, the recommended version is \verb|Open MPI 3.0.0|.
Execute the following commands to install Open MPI locally. 

\begin{lstlisting}
  mkdir -p ~/cloudmesh/bin/openmpi
  cd ~/cloudmesh/bin/openmpi
  wget https://www.open-mpi.org/software/ompi/v3.0/downloads/openmpi-3.0.0.tar.gz  
\end{lstlisting}

Add environmental variables to bashrc file.

\begin{lstlisting}
  emacs ~/.bashrc
  mkdir ~/cloudmesh/bin/openmpi/build
  BUILD=~/cloudmesh/bin/openmpi/build
  OMPI_300=~/cloudmesh/bin/openmpi
  PATH=$BUILD/bin:$PATH
  LD_LIBRARY_PATH=$BUILD/lib:$LD_LIBRARY_PATH
  export BUILD OMPI_300 PATH LD_LIBRARY_PATH
\end{lstlisting}

\begin{lstlisting}
  source ~/.bashrc
\end{lstlisting}

Next build the OpenMPI 3.0.0,

\begin{lstlisting}
  cd $OMPI_300
  ./configure --prefix=$BUILD --enable-mpi-java
  make;make install
\end{lstlisting}

Make sure the installation is successfull by executing,

\begin{lstlisting}
  mpirun --version
\end{lstlisting}

Then you will see an ouput,

\begin{lstlisting}
  mpirun (Open MPI) 3.0.0
\end{lstlisting}

Install the following command to add this as an maven artifact,

\begin{lstlisting}
  mvn install:install-file -DcreateChecksum=true -Dpackaging=jar -Dfile=$OMPI_300/ompi/mpi/java/java/mpi.jar -DgroupId=ompi -DartifactId=ompijavabinding -Dversion=3.0.0
\end{lstlisting}


\subsubsection{Bazel Installation}\label{s:s:twister2-bazel}

For this installation, \verb|Bazel 0.8.1| is recommended.
Execute the following commands to install Bazel,

\begin{lstlisting}
  mkdir -p ~/cloudmesh/bin/bazel
  cd ~/cloudmesh/bin/bazel
  wget https://github.com/bazelbuild/bazel/releases/download/0.8.1/bazel-0.8.1-installer-linux-x86_64.sh
  chmod +x bazel-0.8.1-installer-linux-x86_64.sh
  ./bazel-0.8.1-installer-linux-x86_64.sh --user
  export PATH=$HOME/bin:$PATH
\end{lstlisting}

\subsubsection{Install Extras}

Install the other requirements as follows,

\begin{lstlisting}
  sudo apt-get install git build-essential automake cmake libtool-bin zip libunwind-setjmp0-dev zlib1g-dev unzip pkg-config python-setuptools -y
  sudo apt-get install  python-dev python-pip
\end{lstlisting}

Now you have successfully installed the required packages.  Let us
compile Twister2.

\subsection{Compiling Twister2}

First clone the repository from Github.

\begin{lstlisting}
  mkdir ~/cloudmesh/twister2
  cd ~/cloudmesh/twister2
  git clone git@github.com:DSC-SPIDAL/twister2.git
  cd twister2
\end{lstlisting}

Now compile the code as follows,

\begin{lstlisting}
  bazel build --config=ubuntu twister2/...
\end{lstlisting}

In order to build packages run the following commands,

\begin{lstlisting}
  bazel build --config=ubuntu //scripts/package:tarpkgs
\end{lstlisting}

You can exctract the bazel-bin/scripts/package/twister2-client.tar.gz to run Twister2.
