\chapter{Data Management}

\FILENAME

Obviously when dealing with big data we may not only be dealing with
data in one format but in many different formats. It is important that
you will be able to master such formats and seamlessly integrate in
your analysis. Thus we provide some simple examples on which different
data formats exist and how to use them.

\section{Formats}

\subsection{Pickle}

Python pickle allows you to save data in a python native format into a file
that can later be read in by other programs. However, the data format
may not be portable among different python versions thus the format is
often not suitable to store information. Instead we recommend for
standrad data to use either json or yaml.

\begin{verbatim}
import pickle

flavor = { "small": 100, 
           "medium": 1000,
           "large": 10000 }

pickle.dump( flavor, open( "data.p", "wb" ) )

\end{verbatim}

To read it back in use

\begin{verbatim}
flavor = pickle.load( open( "data.p", "rb" ) )
\end{verbatim}

\subsection{Text Files}

To read text files into a variable called content  you can use 

\begin{verbatim}
content = open(“filename.txt”, “r”).read() 
\end{verbatim}

You can also use the following code while using the convenient
\verb|with| statement

\begin{verbatim}
with open('filename.txt','r') as file:
    content = file.read()
\end{verbatim}

To split up the lines of the file into an array you can do

\begin{verbatim}
with open('filename.txt','r') as file:
    lines = file.read().splitlines()
\end{verbatim}


This cam aslo be done with the build in \verb|readlines| function
\begin{verbatim}
lines = open('filename.txt','r').readlines()
\end{verbatim}

In case the file is too big you will want to read the file line by
line:

\begin{verbatim}
with open('filename.txt','r') as file:
    line = file.readline()
    print (line)
\end{verbatim}


\subsection{CSV Files}

Often data is contained in comma separated values (CSV) within a
file. To read such files you can use the csv package.

\begin{verbatim}
import csv
with open(‘data.csv’, ‘rb’) as f:
   contents = csv.reader(f)
for row in content:
    print row
\end{verbatim}

Using pandas you can read them as follows.

\begin{verbatim}
import pandas as pd
df = pd.read_csv("example.csv") 
\end{verbatim}

There are many other modules and libraries that include CSV read
functions. IN case you need to split a single line by comma, you may
also use the \verb|split| function. However, remember it swill split
at every comma, including those contained in quotes. SO this method
although looking originally convenient has limitations.

\subsection{Excel spread sheets}

Pandas contains a method to read Excel files

\begin{verbatim}
import pandas as pd
filename = 'data.xlsx'
data = pd.ExcelFile(file)
df = data.parse('Sheet1')
\end{verbatim}

\subsection{YAML}

YAML is a very important format as it allows you easily to structure
data in hierarchical fileds It is frequently used to coordinate
programs while using yaml as the specification for configuration fils,
but also data files. To read in a yaml file the following code can be
used

\begin{verbatim}
import yaml
with open('data.yaml', 'r') as f:
    content = yaml.load(f)
\end{verbatim}

The nice part is that this code can also be used to verify if a file
is valid yaml. To write data out we can use

\begin{verbatim}
with open('data.yml', 'w') as f:
    yaml.dump(data, f, default_flow_style=False)
\end{verbatim}

The flow style set to false formats the data in a nice readable
fashion with indentations.


\subsection{JSON}

\begin{verbatim}
import json
with open('strings.json') as f:
    content = json.load(f)
\end{verbatim}

\subsection{XML}

\TODO{Tutorial: Please contribute a XML python tutorial.}

\subsection{RDF}

To read RDF files you will need to install RDFlib with 

\begin{verbatim}
pip install rdflib
\end{verbatim}

This will than allow you to read RDF files

\begin{verbatim}
from rdflib.graph import Graph
g = Graph()
g.parse("filename.rdf", format="format")
for entry in g:
   print(entry)
\end{verbatim}

Good examples on using RDF are provided on the RDFlib Web page
at~\url{https://github.com/RDFLib/rdflib}

From the Web page we showcase also how to directly process RDF data
from the Web

\begin{verbatim}
import rdflib
g=rdflib.Graph()
g.load('http://dbpedia.org/resource/Semantic_Web')

for s,p,o in g:
    print s,p,o
\end{verbatim}

\subsection{PDF}

The Portable Document Format (PDF) has been made available by Adobe
Inc. royalty free. This has enabled PDF to become a world wide adopted
format that also has been standardized in 2008 (ISO/IEC 32000-1:2008,
\url{https://www.iso.org/standard/51502.html}).  A lot of research is
published in papers making PDF one of the de-facto standards for
publishing. However, PDF is difficult to parse and is focused on high
quality output instead of data representation. Nevertheless,
tools to manipulate PDF exist:

\begin{description}
\item[PDFMiner] \url{https://pypi.python.org/pypi/pdfminer/} allows
  the simple translation of PDF into text that than can be further
  mined. The manual page helps to demonstrate some examples
  \url{http://euske.github.io/pdfminer/index.html}.

\item[pdf-parser.py]
  \url{https://blog.didierstevens.com/programs/pdf-tools/} parses pdf
  documents and identifies some structural elements that can than be
  further processed.

\end{description}

If you know about other tools, let us know.


\subsection{HTML}

A very powerful library to parse HTML Web pages is provided
with~\url{https://www.crummy.com/software/BeautifulSoup/}

More details about it are provided in the documentation page
\url{https://www.crummy.com/software/BeautifulSoup/bs4/doc/}

\TODO{Students: beautiful soup contribute tutorial}

\subsection{ConfigParser}

\URL{https://pymotw.com/2/ConfigParser/}

\subsection{ConfigDict}

\URL{https://github.com/cloudmesh/cloudmesh.common/blob/master/cloudmesh/common/ConfigDict.py}

\section{Encryption}

Often we need to protect the information stored in a file. This is
achieved with encryption. There are many methods of supporting
encryption and even if a file is encrypted it may be target to
attacks. Thus it is not only important to encrypt data that you do not
want others to se but also to make sure that the system on which the
data is hosted is secure. This is especially important if we talk
about big data having a potential large effect if it gets into the
wrong hands. 

To illustrate one type of encryption that is non trivial we have
chosen to demonstrate how to encrypt a file with an ssh key. In case
you have openssl installed on your system, this can be achieved as follows.


\begin{verbatim}
#! /bin/sh

# Step 1. Creating a file with data
echo "Big Data is the future." > file.txt

# Step 2. Create the pem 
openssl rsa -in ~/.ssh/id_rsa -pubout  > ~/.ssh/id_rsa.pub.pem

# Step 3. look at the pem file to illustrate how it looks like (optional)
cat ~/.ssh/id_rsa.pub.pem

# Step 4. encrypt the file into secret.txt
openssl rsautl -encrypt -pubin -inkey ~/.ssh/id_rsa.pub.pem -in file.txt -out secret.txt

# Step 5. decrypt the file and print the contents to stdout
openssl rsautl -decrypt -inkey ~/.ssh/id_rsa -in secret.txt
\end{verbatim}

Most important here are Step 4 that encrypts the file and Step 5 that
decrypts the file. Using the Python os module it is straight forward
to implement this. However, we are providing in cloudmesh a convenient
class that makes the use in python very simple.

\begin{verbatim}
from cloudmesh.common.ssh.encrypt import EncryptFile

e = EncryptFile('file.txt', 'secret.txt')
e.encrypt()
e.decrypt()
\end{verbatim}

In our class we initialize it with the locations of the file that is
to be encrypted and decrypted. To initiate that action just call the
methods \verb|encrypt| and \verb|decrypt|.

\section{Database Access}\label{database-access}

\TODO{Students: define conventional database access tutorial}

see: \url{https://www.tutorialspoint.com/python/python_database_access.htm}

\section{SQLite}

\TODO{Students: defineSQLite database access tutorial}

\url{https://www.sqlite.org/index.html}

\url{https://docs.python.org/3/library/sqlite3.html}

\subsection{Exercises}

\begin{exercise}
\label{E:Encryption.1} Test out the shell script to replicate how this
  example works
\end{exercise}

\begin{exercise}
  \label{E:Encryption.2} Test out the cloudmesh encryption class
\end{exercise}

\begin{exercise}
  \label{E:Encryption.3} What other encryption methods exist. Can you
  provide an example and contribute to the section?
\end{exercise}

\begin{exercise}
  \label{E:Encryption.4} What is the issue of encryption that make it
  challenging for Big Data
\end{exercise}

\begin{exercise}
  \label{E:Encryption.5} Given a test dataset with many files text
  files, how long will it take to encrypt and decrypt them on various
  machines. Write a benchmark that you test. Develop this benchmark as
  a group, test out the time it takes to execute it on a variety of
  platforms.
\end{exercise}
