\FILENAME

\section{ENGR-E616 Advanced Cloud Computing}

\TODO{THIS WILL CHANGE}

\subsection{Course Description }

This course describes Cloud 3.0 in which DevOps, Microservices, and
Function as a Service is added to basic cloud computing. The
discussion is centered around the Apache Big Data Stack and a major
student project aimed at demonstrating integration of cloud
capabilities.

\subsection{Course pre-requisites}

Python will be used as a Programming Languages. It is expected that
youknow a programming lanuguage. ENGR-E516 or introduction to cloud
computing required

\subsection{Justification}

Intelligent Systems Engineering is a department and a major at indiana
University. This course is for students who are interested in any
component of the Masters or Ph.D. in Intelligent Systems Engineering.
It is an advanced elective class


\subsection{Teaching and learning methods}

\begin{itemize}
\item	Lectures
\item	6 Assignments including specific lab activities
\item	Final project with help sessions
\item	Class will manipulate lots of software mainly written in Java. However emphasis is use of scripting environments to produce systems. This will use Python and Linux shells.
\end{itemize}

\subsection{Representative bibliography}

\begin{itemize}
\item	\url{http://bigdataopensourceprojects.soic.indiana.edu/}
\item	The backdrop for course is the ~350 software subsystems illustrated at \url{http://hpc-abds.org/kaleidoscope/}
\item	\url{http://cloudmesh.github.io/introduction_to_cloud_computing/}
\item	There are a huge number of web resources
\end{itemize}

\subsection{Student learning outcomes}

When students complete this course, they should be able to:

\begin{itemize}
\item	Have an advanced understanding of issues involved in designing and applying modern cloud technologies using the latest developments.
\item	Gain hands-on laboratory experience with 10-20 software systems.
\item	Understand the Apache Big Data Software Stack.
\item	Apply knowledge of mathematics, science, and engineering
\item	Understand research challenges and important application areas of clouds
\item	Have advanced skills in teamwork with peers.
\end{itemize}

\subsection{Grading}

Grade Item	Percentage
\begin{tabular}{lr}
Assignments	  & 30\% \\
Final Project	& 60\% \\
Participation	& 10\% \\
\end{tabular}

\subsection{Course Content/ Topics covered} 

\begin{table}[h]
\centering
\caption{Course Content}
\label{T:e616}
\begin{tabular}{p{1cm}p{4cm}p{6cm}p{2cm}}
Weeks & Topic                  & Details and Activities                                                           & Assignments                   \\
\hline
1     & Introduction           & Level set on knowledge and status of cloud computing                             & Problem set                   \\
2     & Big Data on Clouds I   & Introduction to Apache Big Data Stack ABDS : Architecture and selected members I & Problem set                   \\
3     & Big Data on Clouds II  & Introduction to Apache Big Data Stack: Architecture and selected members II      & Introductory Software session \\
4     & Cloud 2.0              & DevOps. Ansible and other tools                                                  & Problem Set                   \\
5     & Solutions II           & Introduce Virtual Software Laboratory                                            & Lab work                      \\
6     & Solutions III          & Generate virtual Cluster                                                         & Lab work                      \\
7     & Prepare for project I  & Students read papers, discuss use cases, solutions                               & Problem Set                   \\
8     & Prepare for project II & Get Project Started                                                              & Define Project                \\
9     & Study Key ABDS I       & Understand key ABDS members defined in DevOps                                    & Problem Set                   \\
10    & Container Models       & Docker, OpenStack                                                                & Project Work                  \\
11    & Cloud 3.0              & Microservices, Events, Functions                                                 & Problem Set                   \\
12    & Integrated Deployment  & Learn how to build systems from Function as a Service Components.                & Project Work                  \\
13    & Further ABDS II        & Continue ABDS members defined in DevOps                                          & Project Work                  \\
14    & Further ABDS III       & Continue ABDS members defined in DevOps                                          & Project Work                  \\
15    & Project Reports        & Demonstrate student projects                                                     & Final Project Report         
\end{tabular}
\end{table}