\FILENAME

\subsection{Integrating Bibliographies}\label{bibliographies}

LaTeX integrates very well with bibtex. There are several pre-formated
styles available. It includes also styles for ACM and IEEE
bibliographies. For the ACM style we recommend that you replace
abbrv.bst with abbrvurl.bst, add hyperref to your usepackages so you can
also display URLs in your citations:

\begin{verbatim}
\bibliographystyle{IEEEtran}
\bibliography{references.bib}
\end{verbatim}

Then you have to run latex and bibtex in the following order:

\begin{verbatim}
latex  file
bibtex file
latex  file
latex  file
\end{verbatim}

or simply call make from our makefile.

The reason for the multiple execution of the latex program is to update
all cross-references correctly. In case you are not interested in
updating the library every time in the writing progress just postpone it
till the end. Missing citations are viewed as {[}?{]}.

Two programs stand out when managing bibliographies: emacs and jabref:

\begin{itemize}
\tightlist
\item
  \url{http://www.jabref.org/}
\end{itemize}

Other programs such as Mendeley, Zotero, and even endnote integrate with
bibtex. However their support is limited, so we recommend that you just
use jabref. Furthermore its free and runs on all platforms.

\subsubsection{jabref}\label{jabref}

Jabref is a very simple to use bibliography manager for LaTeX and other
systems. It can create a multitude of bibliography file formats and
allows upload in other online bibliography managers.

\begin{itemize}
\tightlist
\item
  Installation: Go to \url{http://www.jabref.org/} and click download
\item
  Video: \url{https://youtu.be/cMtYOHCHZ3k}
\item
  Video with cc: \url{https://www.youtube.com/watch?v=QVbifcLgMic}
\end{itemize}

\subsubsection{jabref and MSWord}\label{jabref-and-msword}

According to others it is possible to integrate jabref references
directly into MSWord. This has been conducted so far however only on a
Windows computer.

We have not tried this ourselves, but give it as a potential option.

Here are the steps the need to be done:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Create the Jabref bibliography just like in presented in the Jabref
  video
\item
  After finishing adding your sources in Jabref, click
  File -\textgreater{} export
\item
  Name your bibliography and choose MS Office 2007(*.xml) as the file
  format. Remember the location of where you saved your file.
\item
  Open up your word document. If you are using the ACM template, go
  ahead and remove the template references listed under
  Section 7. References
\item
  In the MS Word ribbon choose `References'
\item
  Choose `Manage Sources'
\item
  Click `Browse' and locate/select your Jabref xml file
\item
  You should now see your references appear in the left side window.
  Select the references you want to add to your document and click the
  `copy' button to move them from the left side window to the right
  window.
\item
  Click the `Close' button
\item
  In the MS Word Ribbon, select `Bibliography' under the References tab
\item
  Click `Insert Bibliography' and your references should appear in the
  document
\item
  Ensure references are of Style: IEEE. Styles are located in the
  References tab under `Manage Sources'
\end{enumerate}

As you can see there is significant effort involve, so we do recommend
you use LaTeX as you can focus there on content rather than dealing with
complex layout decisions. This is especially true, if your papers have
figures or tables, or you need to add references.


\section{Entry types}

In this section we will explain how to find and properly generate
bibliographic entries. We are using bibtex for this as it is easy to use
and generates reasonable entries that can be included in papers. What we
like to achieve in this section is not to just show you a final entry,
but to document the process on how that entry was derived. This will
allow you to replicate or learn from the process to apply to your own
entries.

We will address a number of important entry types which includes:

\begin{itemize}
\tightlist
\item
  wikipedia entries
\item
  github entries
\item
  books
\item
  articles in a scientific journal
\item
  articles in a conference
\item
  articles in magazines (non scientific)
\item
  blogs
\end{itemize}

\subsection{Source code References}\label{source-code-references}

We will learn how to cite a source code from a publicly hosted
repository. Such repositories are frequently used and include, for
example github, bitbucket, sourcefore, or your Universities code
repository as long as it is publicly reachable. As changes can occur on
these repositories, it is important that the date ov access is listed in
the entry or even the release version of the source code.

Let us without bias chose a random source dode entry that has been
contributed by a student as follows:

\begin{verbatim}
@Misc{gonzalez_2015,
  Title =  {Buildstep},
  Author =     {Gonzalez, Jose and Lindsay,Jeff},
  HowPublished = {Web Page},
  Month =  {Jul},
  Note =   {Accessed: 2017-1-24},
  Year =   2015,
  Key =        {www-buildstep},
  Url =        {https://github.com/progrium/buildstep}
}
\end{verbatim}

Is this entry correct? Let us analyse.

\subsubsection{Entry type Misc}\label{entry-type-misc}

First, it seems appropriate to use a \emph{@misc} entry. We correctly
identify this is a misc entry as it is online available. More recent
version of bibtex include also the type \emph{@online} for it. However,
in order to maintain compatibility to older formats we chose simply Misc
here and if we really would need to we could replace it easily

\subsubsection{Label}\label{label}

Typically the Label should contain 3 letters from an author name, short
year and the short name of the publication to provide maximum
information regarding the publication. Underscores need to be replaced
by dashes or removed. However as this is a github repository it is
better to integrate this into the label. Hence, we simply use the
github-projectname (in our case github-buildstep, out of convention we
only use lower case letters.

\subsubsection{Author}\label{author}

Unless the last name contains spaces, it should be first name followed
by the last name with multiple authors separated with ``and''.

\subsubsection{Key}\label{key}

In this case the key field can be removed as the entry has an author
field entry. If there was no author field, we could use key to specify
the alphabetical ordering based on the specified key. Note that a key is
not the label. In fact in our original entry the key field was wrongly
used and the student did not understand that the key is used for
sorting.

\subsubsection{Howpublished}\label{howpublished}

Since the source is a github project repository, the howpublished field
shall hold the value \{Code Repository\} rather than a web page. If the
url specified was a normal webpage, the \{Web Page\} entry would be
valid.

\subsubsection{Month}\label{month}

The lowercase month is, used for international notation since months are
not capitalized in some other languages.

\subsubsection{Owner}\label{owner}

In class we introduced the convention to put the student HID in it. If
multiple students contributed, add them with space separation.

\subsubsection{Accessed}\label{accessed}

As we do not yet typically an accessed field, we simply include it in
the note field. This is absolutely essential as code can change and when
we read the code we looked at a particular snapshot in time. In addition
it is often necessary to record the actual version of the code.
Typically this can also be done with the month and year field while
relying on a release date

\subsubsection{Final Entry}\label{final-entry}

Filling out as many fields as possible with information for this entry
we get:

\begin{verbatim}
@Misc{github-buildstep,
  Title =  {Buildstep},
  Author =     {Jose Gonzalez and Jeff Lindsay},
  HowPublished = {Code Repository},
  Year =   {2015},
  Month =  jul,
  Note =   {Accessed: 2017-1-24},
  Url =    {https://github.com/progrium/buildstep},
  Owner =  {S17-IO-3025},
}
\end{verbatim}

We are using the release date in the year and month field as this
project uses this for organizing releases. However, other project may
have release versions so you would have in addition to using the data
also to include the version in the note field such as:

\begin{verbatim}
Note =     {Version: 1.2.3, Accessed: 2017-1-24},
\end{verbatim}

\begin{description}
\item[All those that helped should add your HID to this entry with]
a space separated from each other
\end{description}

\subsection{Researching proper bibtex
entries}\label{researching-proper-bibtex-entries}

\subsubsection{Article in a journal}\label{article-in-a-journal}

Many online bibtex entries are wrong or incomplete. Often you may find
via google a bibtex entry that may need some more research. Lets assume
your first google query returns a publication and you cite it such as
this:

\begin{verbatim}
@Unpublished{unpublished-google-sawzall,
    Title = {{Interpreting the Data: Parallel Analysis with Sawzall}},
    Author = {{Rob Pike, Sean Dorward, Robert Griesemer, Sean Quinlan}},
    Note = {accessed 2017-01-28},
    Month = {October},
    Year = {2005},
    Owner = {for the purpose of this discussion removed},
    Timestamp = {2017.01.31}
}
\end{verbatim}

Could we improve this entry to achieve your best? We observe:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  The author field has a wrong entry as the , is to be replaced by an
  and.
\item
  The author feild has authors and thus must not have a \{\{ \}\}
\item
  The url is missing, as the simple google search actually finds a PDF
  document.
\end{enumerate}

Let us investigate a bit more while searching for the title. We find

\begin{enumerate}
\def\labelenumi{\Alph{enumi})}
\tightlist
\item
  \url{https://www.google.com/url?sa=t\&rct=j\&q}=\&esrc=s\&source=web\&cd=1\&ved=0ahUKEwj\_ytSA-PDRAhUH8IMKHaomC-oQFggaMAA\&url=https\%3A\%2F\%2Fresearch.google.com\%2Farchive\%2Fsawzall-sciprog.pdf\&usg=AFQjCNHSSfKBwbxVAVPQ0td4rTjitKucpA\&sig2=vbiVzi36B3gGFjIzlUKBDA\&bvm=bv.146073913,d.amc
\item
  \url{https://research.google.com/pubs/pub61.html}
\item
  \url{http://dl.acm.org/citation.cfm?id=1239658}
\end{enumerate}

Let us look at A)

As you can see from the url this is actually some redirection to a google
web page which probably is replaced by B as its from google research. So
let us look at B)

Now when you look at the link we find the url
\url{https://research.google.com/archive/sawzall-sciprog.pdf} which
redirects you to the PDF paper.

When we go to B) we find surprisingly a bibtex entry as follows:

\begin{verbatim}
@article{61,
  title = {Interpreting the Data: Parallel Analysis with Sawzall},
  author = {Rob Pike and Sean Dorward and Robert Griesemer and Sean Quinlan},
  year = 2005,
  URL = {https://research.google.com/archive/sawzall.html},
  journal = {Scientific Programming Journal},
  pages = {277--298},
  volume = {13}
}
\end{verbatim}

Now we could say lets be satisfied, but C) seems to be even more
interesting as its from a major publisher. So lats just make sure we
look at C)

If you go to C, you find under the colored box entitled Tools and
Resources a link called \textbf{bibtex}. Thus it seems a good idea to
click on it. This will give you:

\begin{verbatim}
@article{Pike:2005:IDP:1239655.1239658,
    author = {Pike, Rob and Dorward, Sean and Griesemer, Robert and Quinlan, Sean},
    title = {Interpreting the Data: Parallel Analysis with Sawzall},
    journal = {Sci. Program.},
    issue_date = {October 2005},
    volume = {13},
    number = {4},
    month = oct,
    year = {2005},
    issn = {1058-9244},
    pages = {277--298},
    numpages = {22},
    url = {http://dx.doi.org/10.1155/2005/962135},
    doi = {10.1155/2005/962135},
    acmid = {1239658},
    publisher = {IOS Press},
    address = {Amsterdam, The Netherlands, The Netherlands},
}
\end{verbatim}

Now we seem to be at a position to combine our search result as neither
entry is sufficient. As the doi number properly specifies a paper (look
up what a doi is) we can replace the url with one that we find online,
such as the one we found in A) Next we see that all field sin B are
already covered in C, so we take C) and add the url. Now as the label is
great and uniform for ACM, but for us a bit less convenient as its
difficult to remember, we just change it while for example using
authors, title, and year information. lets also make sure to do mostly
lowercase in the label just as a convention. Thus our entry looks like:

\begin{verbatim}
@article{pike05swazall,
    author = {Pike, Rob and Dorward, Sean and Griesemer, Robert and Quinlan, Sean},
    title = {Interpreting the Data: Parallel Analysis with Sawzall},
    journal = {Sci. Program.},
    issue_date = {October 2005},
    volume = {13},
    number = {4},
    month = oct,
    year = {2005},
    issn = {1058-9244},
    pages = {277--298},
    numpages = {22},
    url = {https://research.google.com/archive/sawzall-sciprog.pdf},
    doi = {10.1155/2005/962135},
    acmid = {1239658},
    publisher = {IOS Press},
    address = {Amsterdam, The Netherlands, The Netherlands},
}
\end{verbatim}

As you can see properly specifying a reference takes multiple google
queries and merging of the results you find from various returns. As
you still have time to correct things I advise that you check your
references and correct them. If the original reference would have been
graded it would have been graded with a ``fail'' instead of a ``pass''.

\subsection{Article in a conference
proceedings}\label{article-in-a-conference-proceedings}

Lets look at a second obvious example that needs improvement:

\begin{verbatim}
@InProceedings{wettinger-any2api,
  Title                    = {Any2API - Automated APIfication},
  Author                   = {Wettinger, Johannes and
                              Uwe Breitenb{\"u}cher
                              and Frank Leymann},
  Booktitle                = {Proceedings of the 5th International
                              Conference on Cloud Computing and
              Services Science},
  Year                     = {2015},
  Pages                    = {475­486},
  Publisher                = {SciTePress},

  ISSN                     = {2326-7550},
  Owner                    = {S17-IO-3005},
  Url                      = {https://pdfs.semanticscholar.org/1cd4/4b87be8cf68ea5c4c642d38678a7b40a86de.pdf}
}
\end{verbatim}

As you can see this entry seems to define all required fields, so we
could be tempted to stop here. But its good to double check. Lets do
some queries against ACM, . and google scholar, so we just type in the
title, and if this is in a proceedings they should return hopefully a
predefined bibtex record for us.

Lets query:

\begin{verbatim}
google: googlescholar Any2API Automated APIfication
\end{verbatim}

We get:

\begin{itemize}
\tightlist
\item
  \url{https://scholar.google.de/citations?view_op=view_citation\&hl=en\&user=j6lIXt0AAAAJ\&citation_for_view=j6lIXt0AAAAJ:8k81kl-MbHgC}
\end{itemize}

On that page we see
\href{https://scholar.google.com/scholar_lookup?title=Automated+drug+dispensing+system+reduces+medication+errors+in+an+intensive+care+setting\&author=Chapuis\&publication_year=2010\#}{Cite}

So we find a PDF at
\url{https://pdfs.semanticscholar.org/1cd4/4b87be8cf68ea5c4c642d38678a7b40a86de.pdf}

Lets click on this and the document includes a bibtex entry such as:

\begin{verbatim}
@inproceedings{Wettinger2015, 
  author= {Johannes Wettinger and Uwe Breitenb{\"u}cher and Frank
       Leymann},
  title = {Any2API - Automated APIfication},
  booktitle = {Proceedings of the 5th International Conference on Cloud
       Computing and Service Science (CLOSER)},
  year = {2015},
  pages = {475--486},
  publisher = {SciTePress}
} 
\end{verbatim}

Now lets add the URL and owner:

\begin{verbatim}
@inproceedings{Wettinger2015, 
  author= {Johannes Wettinger and Uwe Breitenb{\"u}cher and Frank
       Leymann},
  title = {Any2API - Automated APIfication},
  booktitle = {Proceedings of the 5th International Conference on Cloud
       Computing and Service Science (CLOSER)},
  year = {2015},
  pages = {475--486},
  publisher = {SciTePress},
  url ={https://pdfs.semanticscholar.org/1cd4/4b87be8cf68ea5c4c642d38678a7b40a86de.pdf},
  owner = {S17-IO-3005},
} 
\end{verbatim}

Should we be satisfied? No, even our original information we gather
provided more information. So lets continue. Lets googlesearch different
queries with ACM or IEEE and the title. When doing the IEEE in the
example we find an entry called

\href{http\%3A\%2F\%2Fdblp.uni-trier.de\%2Fpers\%2Fl\%2FLeymann\%3AFrank\&usg=AFQjCNHCu-66qxWH0zRlPLr4DA8jIo5V-g\&sig2=1vYdnGOEiMcLBEMpbeBA7g}{dlp:
Frank Leyman}

Lets look at it and we find two entries:

\begin{verbatim}
@inproceedings{DBLP:conf/closer/WettingerBL15,
  author    = {Johannes Wettinger and
       Uwe Breitenb{\"{u}}cher and
       Frank Leymann},
  title     = {{ANY2API} - Automated APIfication - Generating APIs for Executables
       to Ease their Integration and Orchestration for Cloud Application
       Deployment Automation},
  booktitle = {{CLOSER} 2015 - Proceedings of the 5th International Conference on
       Cloud Computing and Services Science, Lisbon, Portugal, 20-22 May,
       2015.},
  pages     = {475--486},
  year      = {2015},
  crossref  = {DBLP:conf/closer/2015},
  url       = {http://dx.doi.org/10.5220/0005472704750486},
  doi       = {10.5220/0005472704750486},
  timestamp = {Tue, 04 Aug 2015 09:28:21 +0200},
  biburl    = {http://dblp.uni-trier.de/rec/bib/conf/closer/WettingerBL15},
  bibsource = {dblp computer science bibliography, http://dblp.org}
}

@proceedings{DBLP:conf/closer/2015,
  editor    = {Markus Helfert and
       Donald Ferguson and
       V{\'{\i}}ctor M{\'{e}}ndez Mu{\-{n}}oz},
  title     = {{CLOSER 2015 - Proceedings of the 5th International Conference on
       Cloud Computing and Services Science, Lisbon, Portugal, 20-22 May,
       2015}},
  publisher = {SciTePress},
  year      = {2015},
  isbn      = {978-989-758-104-5},
  timestamp = {Tue, 04 Aug 2015 09:17:34 +0200},
  biburl    = {http://dblp.uni-trier.de/rec/bib/conf/closer/2015},
  bibsource = {dblp computer science bibliography, http://dblp.org}
}
\end{verbatim}

So lets look at the entry and see how to get a better one for our
purpose to combine them. When using jabref, you see optional and
required fields, we want to add as many as possible, regardless if
optional or required, so Lets do that (I I write here in ASCII as easier
to document:

\begin{verbatim}
@InProceedings{,
  author =   {},
  title =    {},
  OPTcrossref =  {},
  OPTkey =   {},
  OPTbooktitle = {},
  OPTyear =      {},
  OPTeditor =    {},
  OPTvolume =    {},
  OPTnumber =    {},
  OPTseries =    {},
  OPTpages =     {},
  OPTmonth =     {},
  OPTaddress =   {},
  OPTorganization = {},
  OPTpublisher = {},
  OPTnote =      {},
  OPTannote =    {},
  url = {}
}
\end{verbatim}

So lets copy and fill out the \textbf{form} from our various searches:

\begin{verbatim}
@InProceedings{Wettinger2015any2api,    
  author    = {Johannes Wettinger and
     Uwe Breitenb{\"{u}}cher and
     Frank Leymann},
  title     = {{ANY2API - Automated APIfication - Generating APIs for Executables
     to Ease their Integration and Orchestration for Cloud Application
     Deployment Automation}},
  booktitle = {{CLOSER 2015 - Proceedings of the 5th International Conference on
       Cloud Computing and Services Science}},
  year =     {2015},
  editor    = {Markus Helfert and
       Donald Ferguson and
       V{\'{\i}}ctor M{\'{e}}ndez Mu{\-{n}}oz},
  publisher = {SciTePress},
  isbn      = {978-989-758-104-5},
  pages = {475--486},
  month = {20-22 May},
  address =      {Lisbon, Portugal},
  doi       = {10.5220/0005472704750486},
  url ={https://pdfs.semanticscholar.org/1cd4/4b87be8cf68ea5c4c642d38678a7b40a86de.pdf},
  owner = {S17-IO-3005},
}
\end{verbatim}

\subsection{What are the differnt entry types and
fields}\label{what-are-the-differnt-entry-types-and-fields}

We were asked what are the different entry types and fields, so we did a
google query and found the following useful information. please remember
that we also have fields such as doi, owner, we will add status
=\{pass/fail\} at time of grading to indicate if the reference passes or
fails. We may assign this to you so you get familiar with the
identification if a refernce is ok or not.

Please see \url{https://en.wikipedia.org/wiki/BibTeX}

\subsection{InProceedings}\label{inproceedings}

Please fill out

\begin{verbatim}
@InProceedings{,
  author =       {},
  title =        {},
  OPTcrossref =  {},
  OPTkey =       {},
  OPTbooktitle = {},
  OPTyear =      {},
  OPTeditor =    {},
  OPTvolume =    {},
  OPTnumber =    {},
  OPTseries =    {},
  OPTpages =     {},
  OPTmonth =     {},
  OPTaddress =   {},
  OPTorganization = {},
  OPTpublisher = {},
  OPTnote =      {},
  OPTannote =    {},
  url = {}
}
\end{verbatim}

\begin{verbatim}
@inproceedings{vonLaszewski15tas,
  author =     {DeLeon, Robert L. and Furlani, Thomas R. and Gallo,
                  Steven M. and White, Joseph P. and Jones, Matthew
                  D. and Patra, Abani and Innus, Martins and Yearke,
                  Thomas and Palmer, Jeffrey T. and Sperhac, Jeanette
                  M. and Rathsam, Ryan and Simakov, Nikolay and von
                  Laszewski, Gregor and Wang, Fugang},
  title =  {{TAS View of XSEDE Users and Usage}},
  booktitle =  {Proceedings of the 2015 XSEDE Conference: Scientific
                  Advancements Enabled by Enhanced
                  Cyberinfrastructure},
  series =     {XSEDE '15},
  year =   2015,
  isbn =   {978-1-4503-3720-5},
  location =   {St. Louis, Missouri},
  pages =  {21:1--21:8},
  articleno =  21,
  numpages =   8,
  url =        {http://doi.acm.org/10.1145/2792745.2792766},
  doi =        {10.1145/2792745.2792766},
  acmid =  2792766,
  publisher =  {ACM},
  address =    {New York, NY, USA},
  keywords =   {HPC, SUPReMM, TAS, XDMoD, XSEDE usage, XSEDE users},
}
\end{verbatim}

\subsection{TechReport}\label{techreport}

Please fill out

\begin{verbatim}
@TechReport{,
  author =       {},
  title =        {},
  institution =  {},
  year =         {},
  OPTkey =       {},
  OPTtype =      {},
  OPTnumber =    {},
  OPTaddress =   {},
  OPTmonth =     {},
  OPTnote =      {},
  OPTannote =    {},
  url = {}    
}
\end{verbatim}

\begin{verbatim}
@TechReport{las05exp,
  title =  {{The Java CoG Kit Experiment Manager}},
  Author =     {von Laszewski, Gregor},
  Institution =    {Argonne National Laboratory},
  Year =   2005,
  Month =  jun,
  Number =     {P1259},
  url = {https://laszewski.github.io/papers/vonLaszewski-exp.pdf}
}
\end{verbatim}

\subsection{Article}\label{article}

Please fill out

\begin{verbatim}
@Article{,
  author =       {},
  title =        {},
  journal =      {},
  year =         {},
  OPTkey =       {},
  OPTvolume =    {},
  OPTnumber =    {},
  OPTpages =     {},
  OPTmonth =     {},
  OPTnote =      {},
  OPTannote =    {},,
  url = {}
}
\end{verbatim}

\begin{verbatim}
@Article{las05gridhistory,
  title =  {{The Grid-Idea and Its Evolution}},
  author =     {von Laszewski, Gregor},
  journal =    {Journal of Information Technology},
  year =   2005,
  month =  jun,
  number =     6,
  pages =  {319-329},
  volume =     47,
  doi =        {10.1524/itit.2005.47.6.319},
  url = {https://laszewski.github.io/papers/vonLaszewski-grid-idea.pdf}
}
\end{verbatim}

\subsection{Proceedings}\label{proceedings}

Please fill out

\begin{verbatim}
@Proceedings{,
  title =        {},
  year =         {},
  OPTkey =       {},
  OPTbooktitle = {},
  OPTeditor =    {},
  OPTvolume =    {},
  OPTnumber =    {},
  OPTseries =    {},
  OPTaddress =   {},
  OPTmonth =     {},
  OPTorganization = {},
  OPTpublisher = {},
  OPTnote =      {},
  OPTannote =    {},
  url = {}
}
\end{verbatim}

\begin{verbatim}
@Proceedings{las12fedcloud-proc,
  title =  {{FederatedClouds '12: Proceedings of the 2012
                  Workshop on Cloud Services, Federation, and the 8th
                  Open Cirrus Summit}},
  year =   2012,
  address =    {New York, NY, USA},
  editor =     {vonLaszewski, Gregor and Robert Grossman and Michael
                  Kozuchand Rick McGeerand Dejan Milojicic},
  publisher =  {ACM},
  iSBN =   {978-1-4503-1754-2},
  location =   {San Jose, California, USA},
  url =
                  {http://dl.acm.org/citation.cfm?id=2378975&picked=prox&cfid=389635474&cftoken=32712991}
}
\end{verbatim}

\subsection{Wikipedia Entry}\label{wikipedia-entry}

Please fill out

\begin{verbatim}
@Misc{,
  OPTkey =       {},
  OPTauthor =    {},
  OPTtitle =     {},
  OPThowpublished = {},
  OPTmonth =     {},
  OPTyear =      {},
  OPTnote =      {},
  OPTannote =    {},
  url = {}
}
\end{verbatim}

\begin{verbatim}
@Misc{www-ode-wikipedia,
  Title =  {Apache ODE},
  HowPublished = {Web Page},
  Note =   {Accessed: 2017-2-11},
  Key =        {Apache ODE},
  Url =        {https://en.wikipedia.org/wiki/Apache_ODE}
}
\end{verbatim}

\subsection{Blogs}\label{blogs}

Please fill out

\begin{verbatim}
@Misc{,
  OPTkey =       {},
  OPTauthor =    {},
  OPTtitle =     {},
  OPThowpublished = {},
  OPTmonth =     {},
  OPTyear =      {},
  OPTnote =      {},
  OPTannote =    {},
  OPTurl = {}
}
\end{verbatim}

\begin{verbatim}
@Misc{www-clarridge-discoproject-blog,
  title =  {Disco - A Powerful Erlang and Python Map/Reduce
                  Framework},
  uthor =  {Clarridge, Tait},
  howpublished = {Blog},
  month =  may,
  note =   {Accessed: 25-feb-2017},
  year =   2014,
  url =  {http://www.taitclarridge.com/techlog/2014/05/disco-a-powerful-erlang-and-python-mapreduce-framework.html}
}
\end{verbatim}

\subsection{Web Page}\label{web-page}

Please fill out

\begin{verbatim}
@Misc{, 
  OPTkey =       {}, 
  OPTauthor =    {}, 
  OPTtitle =     {}, 
  OPThowpublished = {}, 
  OPTmonth =     {}, 
  OPTyear =      {}, 
  OPTnote =      {},
  OPTannote =    {},
  url = {}
}
\end{verbatim}

\begin{verbatim}
@Misc{www-cloudmesh-classes,
  OPTkey =       {},
  author =    {von Laszewski, Gregor},
  title =     {Cloudmesh Classes},
  howpublished = {Web Page},
  OPTmonth =     {},
  OPTyear =      {},
  OPTnote =      {},
  OPTannote =    {},
  url = {https://cloudmesh.github.io/classes/}
}
\end{verbatim}

\begin{verbatim}
@Misc{www-awslambda,
  title =  {AWS Lambda},
  author =     {{Amazon}},
  key =        {AWS Lambda},
  howpublished = {Web Page},
  url =        {https://aws.amazon.com/lambda/faqs/}
}
\end{verbatim}

\subsection{Book}\label{book}

Given the following entry. What is the proper entry for this book.
Provide rationale:

\begin{verbatim}
@Book{netty-book,
    Title = {Netty in Action},
    Author = {Maurer, Norman and Wolfthal, Marvin},
    Publisher = {Manning Publications},
    Year = {2016},
}
\end{verbatim}

To obtain the record of a book you can look at many information sources.
The can include:

\begin{itemize}
\tightlist
\item
  \url{https://www.manning.com/books/netty-in-action}
\item
  \url{https://www.amazon.com/Netty-Action-Norman-Maurer/dp/1617291471}
\item
  \url{http://www.barnesandnoble.com/w/netty-in-action-norman-maurer/1117342155?ean=9781617291470\#productInfoTabs}
\item
  \url{http://www.powells.com/book/netty-in-action-9781617291470/1-0}
\end{itemize}

Furthermore, we need to consider the entry of a book, we simply look it
up in emacs where we find the following but add the owner and the url
field:

\begin{verbatim}
@Book{,
  ALTauthor =      {},
  ALTeditor =      {},
  title =      {},
  publisher =      {},
  year =   {},
  OPTkey =     {},
  OPTvolume =      {},
  OPTnumber =      {},
  OPTseries =      {},
  OPTaddress =     {},
  OPTedition =     {},
  OPTmonth =   {},
  OPTnote =    {},
  OPTannote =      {},
  ownwer =       {},
  url = {}
}
\end{verbatim}

In summary we find the following fields:

\begin{description}
\item[Required fields:]
author/editor, title, publisher, year
\item[Optional fields:]
volume/number, series, address, edition, month, note, key
\end{description}

We apply the following to fill out the fields.

\begin{description}
\item[address:]
The address is the Publisher's address. Usually just the city, but can
be the full address for lesser-known publishers.
\item[author:]
The name(s) of the author(s) (in the case of more than one author,
separated by and) Names can be written in one of two forms: Donald E.
Knuth or Knuth, Donald E. or van Halen, Eddie. Please note that Eddie
van Halen would result in a wrong name. For our purpose we keep nobelity
titles part of the last name.
\item[edition:]
The edition of a book, long form (such as ``First'' or ``Second'')
\item[editor:]
The name(s) of the editor(s)
\item[key:]
A hidden field used for specifying or overriding the alphabetical order
of entries (when the ``author'' and ``editor'' fields are missing). Note
that this is very different from the key that is used to cite or
cross-reference the entry.
\item[label:]
The label field should contain three letters from the auth field, a
short year reference and a short name of the publication to provide the
maximum information regarding the publication. Underscores should be
replaced with dashes or removed completely.
\item[month:]
The month of publication or, if unpublished, the month of creation. Use
three-letter abbreviations for this field in order to account for
languages that do not capitalize month names. Additional information for
the day can be included as follows: aug \#``\textasciitilde{}10,''
\item[publisher:]
The publisher's name
\item[series:]
The series of books the book was published in (e.g. ``The Hardy Boys''
or ``Lecture Notes in Computer Science'')
\item[title:]
The title of the work. As the capitalization depends on the bibliography
style and the language used we typically use camel case. To force
capitalization of a word or its first letter you can use the curly
braces, `\{ \}'. To keep the title in camel case simple use title =
\{\{My Title\}\}
\item[type:]
The field overriding the default type of publication (e.g. ``Research
Note'' for techreport, ``\{PhD\} dissertation'' for phdthesis,
``Section'' for inbook/incollection) volume The volume of a journal or
multi-volume book year The year of publication (or, if unpublished, the
year of creation)
\end{description}

While applying the above rules and tips we summarize what we have done
for this entry:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Search for the book by title/Author on ACM (\url{http://dl.acm.org/})
  or Amazon or barnesandnoble or upcitemdb (\url{http://upcitemdb.com}).
  These services return bibtex entrie that you can improve.
\item
  Hence one option is t get the ISBN of the book. For ``Mesos in
  action'' from upcitemdb we got the ISBN as ``9781617 292927''. This is
  the 13 digit ISBN. The first 3 digits (GS1 code) can be skipped. Using
  the rest of 10 digits ``1617 292927'', Add in JabRef in Optional
  Fields-\textgreater{}ISBN.

  However it is fine to youst specify the full number.

  We can also return a bibtex entry generated while using Click on the
  ``Get BibTex from ISBN''.

  Now we get more information on this book entry from ISBN. We can opt
  either the original or newly searched entry for the below bibtex
  fields or merge as appropriate. URL may not match from where we
  initially read the book, however there is option to put your original
  url or newly searched url. EAN, Edition, Pages,url,published date etc.
  Do a search on amazon for ``ASIN''. Can skip if not available.
  Sometime we get ASIN for a different publication, maybe a paperback
  ASIN=\{B01MT311CU\} We can add it as it becomes easier to search
\end{enumerate}

\begin{description}
\item[doi:]
If you can find a doi numer you should also add it. IN this case we
could not locate one.
\end{description}

As a result we obtain the entry:

\begin{verbatim}
@Book{netty-book,
  title = {Netty in Action},
  publisher = {Manning Publications Co.},
  year = {2015},
  author = {Maurer, Norman and Wolfthal, Marvin Allen},
  address = {Greenwich, CT, USA},
  edition = {1st},
  isbn = {1617291471},
  asin = {1617291471},
  date = {2015-12-23},
  ean = {9781617291470},
  owner = {S17-IO-3022 S17-IO-3010 S17-IO-3012},
  pages = {296},
  url = {http://www.ebook.de/de/product/21687528/norman_maurer_netty_in_action.html},
}
\end{verbatim}

\section{Integrating Bibtex entries into Other Systems}

We have not tested any of this
\subsection{Bibtex import to MSWord}\label{bibtex-import-to-msword}


\subsubsection{XML import}\label{xml-import}

Plaease respond back to us if you have used this and give feedback.

\begin{enumerate}

\item  In JabRef, export the bibliography in MS Word 2008 xml format

\item  Name the file Sources.xml (case sensitive)
\item   In OSX with MS Word 2015: Go to
  \verb|/Library/Containers/com.microsoft.word/Data/Library/Application Support/Microsoft/Office.|
\item  Rename the original Sources.xml file to Sources.xml.bak
\item  Copy the generated Sources.xml in this folder
\item  Restart MS Word.

\end{enumerate}

We do not know what needs to be done in case you need to make changes to
the refernces. Please report back your experiences. To avoid issues we
recommend that you use LaTeX. and not MSWord.

\subsubsection{BibTex4Word}\label{bibtex4word}

We have not tried this:

\URL{http://www.ee.ic.ac.uk/hp/staff/dmb/perl/index.html}


You are highly recommended to use Jabref for bibliography management in
this class. Here is an introductory video on Jabref:
\url{https://youtu.be/roi7vezNmfo?t=8m6s}

\section{Other Reference Managers}\label{other-reference-managers}

Please note that you should first decide which reference manager you
like to use. In case you for example install zotero and mendeley, that
may not work with word or other programs.

\subsection{Endnote}\label{endnote}

Endnote os a reference manager that works with Windows. Many people use
Endnote. However, in the past, Endnote has caused complications when
dealing with collaborative management of references. Its price is
considerable. We have lost many hours of work because of instability of
Endnote in some cases. As a student, you may be able to use Endnote for
free at Indiana University.

\URL{http://endnote.com/}


\subsection{Mendeley}\label{mendeley}

Mendeley is a free reference manager compatible with Windows Word 2013,
Mac Word 2011, LibreOffice, BibTeX. Videos on how to use it are
available at:

\URL{https://community.mendeley.com/guides/videos}


Installation instructions are available at

\URL{https://www.mendeley.com/features/reference-manager/}


When dealing with large databases, we found the integration of Mendeley
into word slow.

\subsection{Zotero}\label{zotero}

Zotero is a free tool to help you collect, organize, cite, and share
your research sources. Documentation is available at

\URL{https://www.zotero.org/support/}

The download link is available from

\URL{https://www.zotero.org/}


We have limited experience with Zotero

\subsection{Paperpile}

Paper pile is a Web based refernce management tool that integrates
with Google docs. It can export the database as bibtex. Paperpile is a
commercial tool cosing about \$36 a year for academic users. For
others it is about 3 times as expensive.

\URL{https://www.zotero.org/support/}