\chapter{Projects}
\label{c:projects}
\index{Projects}
\FILENAME\

\section{Class: E222}

For the final project in this class you need to do the following.

\begin{itemize}
\item Find a dataset : Sample Data Repositories \URL{https://archive.ics.uci.edu/ml/datasets.html}
\item Select a suitable dataset.
\item Use Scikit Learn Library to run Machine Learning algorithsm depending on your problem.
\item Do some classifications, clustering or a regression calculation using a machine learning algorithm.
\item Use the results from classification to draw charts. You can use matplotlib to do this.
\item Use Flask Rest API to expose the data to the viewers. So people can send a data set and get the outputs as a json object.   
\end{itemize}


\subsection{Simple Explained Project}

First select a simple data set like Adult data set from the above Data
Repository. If you read through the description in the data set, you
can find out that this data set is a classifiable data set. And also
it says there are 14 attributes per each data sample and there are
48842 data points with multiple classes. For the classification
problem, you can use an algorithm like Support Vector Machines and do
the classification using scikit learn SVM
\URL{http://scikit-learn.org/stable/modules/svm.html}. Or you can view
this problem as a regression problem if you want to predict the age of
a particular person
\URL{http://scikit-learn.org/stable/modules/generated/sklearn.linear_model.LinearRegression.html}.

First you need to clean up the data. For instance consider the following data point in the data set. 

\begin{lstlisting}
32,  Private, 205019, Assoc-acdm, 12, Never-married, Sales, Not-in-family, Black, Male, 0, 0, 50, United-States, <=50K
\end{lstlisting}

The expected output for this set of features is the age 32.

In your programme first you need to separate age column to a seaparte
file like y.csv and keep features in a file called, x.csv.
\begin{lstlisting}
Features: Private, 205019, Assoc-acdm, 12, Never-married, Sales, Not-in-family, Black, Male, 0, 0, 50, United-States, <=50K
Expected Output : 32
\end{lstlisting}

So you will be feeding x.csv as feature data and y.csv as
corresponding outputs. We do this because, the ML algorithms only
understand numbers.

But there is an important thing that you need to do when cleaning up
the data in the early stages of the project. Choose numerical values
for string fields.  For instance workclass or the first attribute in
the feature vector.  workclass: Private, Self-emp-not-inc,
Self-emp-inc, Federal-gov, Local-gov, State-gov, Without-pay,
Never-worked.  You can pick values as Private = 0, Self-emp-not-inc =
1, etc. Data preprocessing will take a longer time, but that has to be done. 


Then we need to show these data to the user in form of tabular or
chart representation. For this purpose you should use Python Pandas
and Matplotlib.  Now you have completed 80 percent of your
project. Then you must give a functionality to users. Now you need to
feed these data to the Linear Regression algorithm and get results and
then use matplotlib to show the regression curve. User submits a datapoint
in form of the original data format.

\begin{lstlisting}
User Input: Private, 205019, Assoc-acdm, 12, Never-married, Sales, Not-in-family, Black, Male, 0, 0, 50, United-States, <=50K
Expected Ouput : 12
Predicted Ouput : 12.5
\end{lstlisting}

This way you can compare the accuarcy of your training model.


\subsection{Deliverables}

\begin{itemize}
\item Original Data Set (Estimated Time 1 hour)
\item Cleaned Up Data Set (Estimated Time 1.5 Week)
\item Scikit Learn ML Algorithm Application (Estimated Time 1 Week)
\item Clustering or Regression or Classification results in Graphical Format (Matplotlib) (GUI not needed, save graphs as png) (Estimated Time 10 hours)
\item Flask Rest Service to send a sample data set and get output (terminal output is enough) (Estimated Time 1 day) (Optional : Bonus points)
\item Create a Makefile with running, setting up, sample test case running commands. (Estimated Time 1 hour)  
\item requirement.txt file for pip installation. (Estimated Time >1 hour)
\item Package with Docker  (Estimated Time 1 hour)
\end{itemize}

Total Estimated Time : 3 weeks.
\subsection{Suggestions}

Use a smaller data set and try to complete the whole exercise. 

