\section{Results}\label{S:results}

In this section we list documents about BigData technologies and
Projects that have been delivered by students of past classes. As we
can not post any grades it is importan that you yourself identify good
examples from the published list. It is important not to make the
mistake to work towards minimal fulfillment of the class requirements,
but instead work towards achieving your best. All documents produced
by this class will be made available on github.com and through this
document. This helps other students to learn from your experience and
to counteract plagiarism. 

\begin{NOTE}
  Examples provided here may not necessarily meet the requirements for
  your current class as the content and requirements have changed
  since the other classes were thought. This includes format of the
  paper, paper length, as well as the topic for projects.
\end{NOTE}

\subsection{Introduction to Big Data Applications and Analytics}

This class was known under the name I523.

% this document needs to be deleted as it is temporary
% \URL{https://github.com/laszewski/laszewski.github.io/raw/master/papers/vonLaszewski-i523.pdf}

Application and Technologies (Vol.1):
\URL{https://github.com/laszewski/laszewski.github.io/raw/master/papers/vonLaszewski-i523-v1.pdf}

Application and Technologies (Vol. 2):
\URL{https://github.com/laszewski/laszewski.github.io/raw/master/papers/vonLaszewski-i523-v2.pdf}

Project: First 500 pages:
\URL{https://github.com/laszewski/laszewski.github.io/raw/master/papers/vonLaszewski-i523-v3-1.pdf}

Project: Second part, starting past page number501:
\URL{https://github.com/laszewski/laszewski.github.io/raw/master/papers/vonLaszewski-i523-v3-2.pdf}

\subsection{Big Data Applications and Open Source Software}

This class was known under the name I524

Big Data Software Vol 1.:
\URL{https://github.com/cloudmesh/sp17-i524/blob/master/paper1/proceedings.pdf}

Big Data Software Vol 2.:
\URL{https://github.com/cloudmesh/sp17-i524/blob/master/paper2/proceedings.pdf}

Big Data Projects:
\URL{https://github.com/cloudmesh/sp17-i524/blob/master/project/projects.pdf}
