\FILENAME

\section{Resources}

In any case please visit the Chameleon Web page as there is also more
information about other topics that we may not care about. Furthermore
we do not use Advanced Appliences, but use ansible instead as it is
independent from OpenStack and can be used with other frameworks.

If you prefer you can also go to the Chameleon Web site using the
following links. However we have improved some of the documentation
found in this document. We would like to get your feedback in case you
find errors or like to contribute tho this documentation.

\begin{WARNING}
  Chameleon cloud promotes insecure use of ssh while suggesting
  passphrase less keys. This is {\bf very dangerous} due to the fact
  that somone could gain access to your computer and if a password
  less key is stolen easy access to other systems can be
  achieved. INstead you must use whenever possible passphrases and use
  ssh agend and ssh add!

  Hence do not use their advise that is mantioned multiple times in
  their documentation. Follow ours!
\end{WARNING}

The links to Chameleons Documentation 

\begin{itemize}
\item
  \href{https://www.chameleoncloud.org/}{Home}
\item
  \href{openstack-kvm-user-guide.html\#}{Documentation }

  \begin{itemize}
    \item
    \href{https://www.chameleoncloud.org/docs/getting-started/}{Getting
    Started}
  \item
    \href{https://www.chameleoncloud.org/docs/bare-metal-user-guide/}{Bare
    Metal}
  \item
    \href{https://www.chameleoncloud.org/docs/complex-appliances/}{Complex
    Appliances}
  \item
    \href{https://www.chameleoncloud.org/docs/openstack-kvm-cloud/}{OpenStack
    KVM Cloud}
  \item
    \href{https://www.chameleoncloud.org/docs/user-faq/}{User FAQ}
  \item
    \href{https://www.chameleoncloud.org/docs/community/}{Community}
  \end{itemize}
\item
  \href{https://www.chameleoncloud.org/appliances/}{Appliances}
\item
  \href{https://www.chameleoncloud.org/hardware/}{Hardware}
\item
  \href{https://www.chameleoncloud.org/news/}{News}
\item
  \href{openstack-kvm-user-guide.html\#}{About }

  \begin{itemize}
    \item
    \href{https://www.chameleoncloud.org/about/chameleon/}{About
    Chameleon}
  \item
    \href{https://www.chameleoncloud.org/about/hardware-description/}{Hardware
    Description}
  \item
    \href{https://www.chameleoncloud.org/talks/}{Talks}
  \item
    \href{https://www.chameleoncloud.org/about/newsletter/}{Stay in
    Touch}
  \item
    \href{https://www.chameleoncloud.org/about/media-resources/}{Media
    Resources}
  \end{itemize}
\end{itemize}

\begin{itemize}
\item
  \href{https://www.chameleoncloud.org/login/}{Log in}
\item
  \href{openstack-kvm-user-guide.html\#}{Users}

  \begin{itemize}
    \item
    \href{https://www.chameleoncloud.org/user/register/}{Register}
  \item
    \href{https://www.chameleoncloud.org/docs/getting-started/experiment-quickstart/}{Experiment}
  \item
    \href{https://www.chameleoncloud.org/user/help/ticket/new/guest/}{Help}
  \end{itemize}
\end{itemize}

