

\chapter{Health Informatics Case Study}

\FILENAME

\slides{Health}{131}{Health Informatics}{https://drive.google.com/open?id=0B6wqDMIyK2P7UGRJNmlkYkNkQk0}

This section starts by discussing general aspects of Big Data and Health
including data sizes, different areas including genomics, EBI, radiology
and the Quantified Self movement. We review current state of health care
and trends associated with it including increased use of Telemedicine.
We summarize an industry survey by GE and Accenture and an impressive
exemplar Cloud-based medicine system from Potsdam. We give some details
of big data in medicine. Some remarks on Cloud computing and Health
focus on security and privacy issues.

We survey an April 2013 McKinsey report on the Big Data revolution in US
health care; a Microsoft report in this area and a European Union report
on how Big Data will allow patient centered care in the future. Examples
are given of the Internet of Things, which will have great impact on
health including wearables. A study looks at 4 scenarios for healthcare
in 2032. Two are positive, one middle of the road and one negative. The
final topic is Genomics, Proteomics and Information Visualization.

\section{Big Data and Health}\label{big-data-and-health}

This lesson starts with general aspects of Big Data and Health including
listing subareas where Big data important. Data sizes are given in
radiology, genomics, personalized medicine, and the Quantified Self
movement, with sizes and access to European Bioinformatics Institute.

\video{Health}{10:02}{Big Data and Health}{https://www.youtube.com/watch?v=ZkM-yZJQ1Cg} 

\section{Status of Healthcare Today}

This covers trends of costs and type of healthcare with low cost genomes
and an aging population. Social media and government Brain initiative.

\video{Health}{16:09}{Status of Healthcare Today}{https://www.youtube.com/watch?v=x9TpdMBqYrk} 

\section{Telemedicine (Virtual Health)}

This describes increasing use of telemedicine and how we tried and
failed to do this in 1994.

\video{Health}{8:21}{Telemedicine}{https://www.youtube.com/watch?v=Pe4CVXQaL_U} 

\begin{comment}
\section{Big Data and Healthcare Industry}

Summary of an industry survey by GE and Accenture.

\video{Health}{10:02}{Big Data and Healthcare Indusry}{https://www.youtube.com/watch?v=64YOUnRJVZU}
\end{comment}

\section{Medical Big Data in the Clouds}

An impressive exemplar Cloud-based medicine system from Potsdam.

\video{Health}{15:02}{Medical Big Data in the Clouds}{https://www.youtube.com/watch?v=GldSVijkJcM} 


\subsection{Medical image Big Data}\label{medical-image-big-data}

\video{Health}{6:33}{Midical Image Big Data}{https://www.youtube.com/watch?v=GOcVtwx2R2k} 

\subsection{Clouds and Health}\label{clouds-and-health}

\video{Health}{4:35}{Clouds and Health}{http://youtu.be/9Whkl_UPS5g}


\subsection{McKinsey Report on the big-data revolution in US health
  care}

This lesson covers 9 aspects of the McKinsey report. These are the
convergence of multiple positive changes has created a tipping point for
innovation; Primary data pools are at the heart of the big data
revolution in healthcare; Big data is changing the paradigm: these are
the value pathways; Applying early successes at scale could reduce US
healthcare costs by \$300 billion to \$450 billion; Most new big-data
applications target consumers and providers across pathways; Innovations
are weighted towards influencing individual decision-making levers; Big
data innovations use a range of public, acquired, and proprietary data
types; Organizations implementing a big data transformation should
provide the leadership required for the associated cultural
transformation; Companies must develop a range of big data capabilities.

\video{Health}{14:53}{McKinsey Report}{https://www.youtube.com/watch?v=fu-TWnIk980} 

\subsection{Microsoft Report on Big Data in Health}

This lesson identifies data sources as Clinical Data, Pharma \& Life
Science Data, Patient \& Consumer Data, Claims \& Cost Data and
Correlational Data. Three approaches are Live data feed, Advanced
analytics and Social analytics.

\video{Health}{2:26}{Microsoft Report on Big Data in Health}{http://youtu.be/PjffvVgj1PE}


\subsection{EU Report on Redesigning health in Europe for 2020}

This lesson summarizes an EU Report on Redesigning health in Europe for
2020. The power of data is seen as a lever for change in My Data, My
decisions; Liberate the data; Connect up everything; Revolutionize
health; and Include Everyone removing the current correlation between
health and wealth.


\video{Health}{5:00}{EU Report on Redesigning health in Europe for 2020}{http://youtu.be/9mbt_ZSs0iw}


\subsection{Medicine and the Internet of Things}

The Internet of Things will have great impact on health including
telemedicine and wearables. Examples are given.

\video{Health}{8:17}{Medicine and the Internet of Things}{https://www.youtube.com/watch?v=Jk3EeFzZnuU}


\subsection{Extrapolating to 2032}

A study looks at 4 scenarios for healthcare in 2032. Two are positive,
one middle of the road and one negative.

\video{Health}{15:13}{Extrapolating to 2032}{https://www.youtube.com/watch?v=a5G4HACeokg} 


\subsection{Genomics, Proteomics and Information Visualization}

A study of an Azure application with an Excel frontend and a cloud BLAST
backend starts this lesson. This is followed by a big data analysis of
personal genomics and an analysis of a typical DNA sequencing analytics
pipeline. The Protein Sequence Universe is defined and used to motivate
Multi dimensional Scaling MDS. Sammon's method is defined and its use
illustrated by a metagenomics example. Subtleties in use of MDS include
a monotonic mapping of the dissimilarity function. The application to
the COG Proteomics dataset is discussed. We note that the MDS approach
is related to the well known chisq method and some aspects of nonlinear
minimization of chisq (Least Squares) are discussed.

\video{Health}{6:56}{Genomics, Proteomics and  Information Visualization}{https://www.youtube.com/watch?v=zGzBtxq1ZRE}

\begin{comment}
\video{Health}{6:56}{ CC) Genomics, Proteomics and  Information Visualization}{https://drive.google.com/file/d/0B5plU-u0wqMoVzduODM0Z2dFYWM/view?usp=sharing}
\end{comment}

Next we continue the discussion of the COG Protein Universe introduced
in the last lesson. It is shown how Proteomics clusters are clearly seen
in the Universe browser. This motivates a side remark on different
clustering methods applied to metagenomics. Then we discuss the
Generative Topographic Map GTM method that can be used in dimension
reduction when original data is in a metric space and is in this case
faster than MDS as GTM computational complexity scales like N not N
squared as seen in MDS.

Examples are given of GTM including an application to topic models in
Information Retrieval. Indiana University has developed a deterministic
annealing improvement of GTM. 3 separate clusterings are projected for
visualization and show very different structure emphasizing the
importance of visualizing results of data analytics. The final slide
shows an application of MDS to generate and visualize phylogenetic
trees.

\TODO{These two videos need to be uploaded to youtube}

\video{Health}{10:33}{Genomics, Proteomics and Information Visualization I}{https://drive.google.com/file/d/0B5plU-u0wqMobXdEQWRHWl95UTA/view?usp=sharing}

\video{Health}{7:41}{Genomics, Proteomics and Information Visualization: II}{https://drive.google.com/file/d/0B5plU-u0wqModlhmdVUwdGlQNTA/view?usp=sharing}

\slides{Health}{131}{Proteomics and Information Visualization}{https://drive.google.com/open?id=0B8936_ytjfjmX0lEMWhMX2kwRHc}
  


\section{Resources}

\TODO{These resources have not all been checked to see if they still
  exist this is curretnly in progress}

\begin{itemize}
\item
  \url{https://wiki.nci.nih.gov/display/CIP/CIP+Survey+of+Biomedical+Imaging+Archives}
\item
  \url{http://grids.ucs.indiana.edu/ptliupages/publications/Where\%20does\%20all\%20the\%20data\%20come\%20from\%20v7.pdf}
\item
  \url{http://www.ieee-icsc.org/ICSC2010/Tony\%20Hey\%20-\%2020100923.pdf}
\item
  \url{http://quantifiedself.com/larry-smarr/}
\item
  \url{http://www.ebi.ac.uk/Information/Brochures/}
\item
  \url{http://www.kpcb.com/internet-trends}
\item
  \url{http://www.slideshare.net/drsteventucker/wearable-health-fitness-trackers-and-the-quantified-self}
\item
  \url{http://www.siam.org/meetings/sdm13/sun.pdf}
\item
  \url{http://en.wikipedia.org/wiki/Calico_\%28company\%29}
\item
  \url{http://www.slideshare.net/GSW_Worldwide/2015-health-trends}
\item
  \url{http://www.accenture.com/SiteCollectionDocuments/PDF/Accenture-Industrial-Internet-Changing-Competitive-Landscape-Industries.pdf}
\item
  \url{http://www.slideshare.net/schappy/how-realtime-analysis-turns-big-medical-data-into-precision-medicine}
\item
  \url{http://medcitynews.com/2013/03/the-body-in-bytes-medical-images-as-a-source-of-healthcare-big-data-infographic/}
\item
  \url{http://healthinformatics.wikispaces.com/file/view/cloud_computing.ppt}
\item
  \url{https://www.mckinsey.com/~/media/mckinsey/industries/healthcare%20systems%20and%20services/our%20insights/the%20big%20data%20revolution%20in%20us%20health%20care/the_big_data_revolution_in_healthcare.ashx}
\begin{comment}
\item
  \url{https://partner.microsoft.com/download/global/40193764}
\end{comment}
\item
  \url{https://ec.europa.eu/eip/ageing/file/353/download_en?token=8gECi1RO}
\item
  \url{http://www.kpcb.com/internet-trends}
\begin{comment}
\item
  \url{http://www.liveathos.com/apparel/app}
\end{comment}
\item
  \url{http://debategraph.org/Poster.aspx?aID=77}
\begin{comment}
\item
  \url{http://www.oerc.ox.ac.uk/downloads/presentations-from-events/microsoftworkshop/gannon}
\end{comment}
\item
  \url{http://www.delsall.org}
\item
  \url{http://salsahpc.indiana.edu/millionseq/mina/16SrRNA_index.html}
\item
  \url{http://www.geatbx.com/docu/fcnindex-01.html}
\item
  \url{https://wiki.nci.nih.gov/display/CIP/CIP+Survey+of+Biomedical+Imaging+Archives}
\item
  \url{http://grids.ucs.indiana.edu/ptliupages/publications/Where\%20does\%20all\%20the\%20data\%20come\%20from\%20v7.pdf}
\item
  \url{http://www.ieee-icsc.org/ICSC2010/Tony\%20Hey\%20-\%2020100923.pdf}
\item
  \url{http://quantifiedself.com/larry-smarr/}
\item
  \url{http://www.ebi.ac.uk/Information/Brochures/}
\item
  \url{http://www.kpcb.com/internet-trends}
\item
  \url{http://www.slideshare.net/drsteventucker/wearable-health-fitness-trackers-and-the-quantified-self}
\item
  \url{http://www.siam.org/meetings/sdm13/sun.pdf}
\item
  \url{http://en.wikipedia.org/wiki/Calico_\%28company\%29}
\item
  \url{http://www.slideshare.net/GSW_Worldwide/2015-health-trends}
\item
  \url{http://www.accenture.com/SiteCollectionDocuments/PDF/Accenture-Industrial-Internet-Changing-Competitive-Landscape-Industries.pdf}
\item
  \url{http://www.slideshare.net/schappy/how-realtime-analysis-turns-big-medical-data-into-precision-medicine}
\item
  \url{http://medcitynews.com/2013/03/the-body-in-bytes-medical-images-as-a-source-of-healthcare-big-data-infographic/}
\item
  \url{http://healthinformatics.wikispaces.com/file/view/cloud_computing.ppt}
\item
  \url{http://www.mckinsey.com/~/media/McKinsey/dotcom/Insights/Health\%20care/The\%20big-data\%20revolution\%20in\%20US\%20health\%20care/The\%20big-data\%20revolution\%20in\%20US\%20health\%20care\%20Accelerating\%20value\%20and\%20innovation.ashx}
\item
  \url{https://partner.microsoft.com/download/global/40193764}
\item
  \url{http://ec.europa.eu/information_society/activities/health/docs/policy/taskforce/redesigning_health-eu-for2020-ehtf-report2012.pdf}
\item
  \url{http://www.kpcb.com/internet-trends}
\item
  \url{http://www.liveathos.com/apparel/app}
\item
  \url{http://debategraph.org/Poster.aspx?aID=77}
\item
  \url{http://www.oerc.ox.ac.uk/downloads/presentations-from-events/microsoftworkshop/gannon}
\item
  \url{http://www.delsall.org}
\item
  \url{http://salsahpc.indiana.edu/millionseq/mina/16SrRNA_index.html}
\item
  \url{http://www.geatbx.com/docu/fcnindex-01.html}
\end{itemize}
